---
title: "MapResPrac - Data Cleaning"
editor: source
editor_options:
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r}
#| warning: false
#| code-fold: true
#| error: false
#| message: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)

question_labels <- readxl::read_xlsx("MapResPrac_correspondance.xlsx")
# names(question_labels)  # Question long names

df <- read.csv("MapResPrac-080426-557.csv")
names(df) <- as.character(as.vector(question_labels[1,])) |>
  str_replace_all(fixed(".  "), "_") |>
  str_replace_all(fixed(". "), "_") |>
  str_replace_all(fixed("."), "_") |>
  str_replace_all(fixed(" "), "_") |>
  str_replace_all(fixed("/"), "_")

format_binary <- function(x) {
  case_when(x == "Yes" ~ 1, x == "No" ~ 0, .default = NA)
}
format_use <- function(x) {
  case_when(x == "I know it and I used it" ~ 3/3,
            x == "I haven't used it yet, but I plan to do it in the future" ~ 2/3,
            x == "I am not familiar with it" ~ 1/3,
            x == "I haven't used it yet, and I don't plan to do it in the future" ~ 0,
            .default = NA)
}


df <- df |>
  select(-contains(" time: ")) |>
  mutate(Dem_Gender = ifelse(Dem_Gender == "Non-binary", "Other", Dem_Gender),
         Dem_Age = ifelse(Dem_Age < 18, NA, Dem_Age),
         OS_Familiar = OS_Familiar / 100,
         OS_Importance = OS_Importance / 100,
         OS_Workshops = format_binary(OS_Workshops),
         OS_Study_Preregistration = format_use(OS_Study_Preregistration),
         OS_Registered_Reports = format_use(OS_Registered_Reports),
         OS_Open_Materials = format_use(OS_Open_Materials),
         OS_Open_Data = format_use(OS_Open_Data),
         OS_Open_Peer_Review = format_use(OS_Open_Peer_Review),
         OS_Open_Access_Publication = format_use(OS_Open_Access_Publication),
         OS_Replication_Studies = format_use(OS_Replication_Studies),
         OS_Participatory_Research = format_use(OS_Participatory_Research),
         OS_Help_More_Information = format_binary(OS_Help_More_information),
         OS_Help_Training = format_binary(OS_Help__training),
         OS_Help_Ethical_Issues = format_binary(OS_Help_ethical_issues),
         OS_Help_Infrastructure = format_binary(OS_Help_infrastructure),
         OS_Help_Time = format_binary(OS_Help_time),
         OS_Help_Workload = format_binary(OS_Help_Workload),
         OS_Help_Funding = format_binary(OS_Help_Funding),
         OS_Help_Incentives_Fund_Institutions = format_binary(OS_Help_Incentives_fund_institutions),
         OS_Help_Recognition_Promotion_Recruitment = format_binary(OS_Help_Recognition_promotion_recruitment),
         OS_Help_Support_Seniors = format_binary(OS_Help_Support_seniors),
         OS_Help_Support_Juniors = format_binary(OS_Help_Support_juniors),
         OS_Help_Positive_Beliefs = format_binary(OS_Help_Positive_beliefs),
         OS_Help_No_Plan_Use_OS = format_binary(OS_Help_No_plan_Use_OS),
         OS_Help_Nothing = format_binary(OS_Help_Nothing),
         # Slow Science
         SS_Familiar = SS_Familiar / 100,
         SS_Importance = SS_Importance / 100,
         SS_Workshops = format_binary(SS_Workshops),
         SS_Definition_Quality_over_quantity = format_binary(SS_Definition_Quality_over_quantity),
         SS_Definition_Slow_Process = format_binary(`SS_Definition__slow_process_over_short-term`),
         SS_Definition_Changing_Metrics = format_binary(SS_Definition_Changing_metrics),
         SS_Definition_Increase_Research_Time = format_binary(SS_Definition_Increase_research_time),
         SS_Definition_Diminishing_Publications = format_binary(SS_Definition_Diminishing_publications),
         SS_Definition_Work_Life_Balance = format_binary(`SS_Definition_work-life_balance`),
         across(starts_with("SS_") & matches("Feasible|Not_Feasible"), ~replace_na(.x, 0)),
         # Green Science
         GS_Importance_conducting = GS_Importance_conducting / 100,
         GS_Importance_topic = GS_Importance_topic / 100,
         GS_Changes_practices = GS_Changes_practices / 100,
         GS_Changes_communication_practices = GS_Changes_communication_practices / 100,
         GS_Relation_Research_Sustainability = GS_Relation_research_sustanability / 100,
         GS_Change_practices_agreeing = GS_Change_practices_agreeing / 100,
         # Ethical Science
         ES_Importance_research_team = ES_Importance_research_team / 100,
         ES_Consequences_society = ES_Consequences_society / 100
         ) |>
  select(-OS_Help__training,
         -OS_Help_More_information,
         -OS_Help_ethical_issues,
         -OS_Help_infrastructure,
         -OS_Help_time,
         -OS_Help_Incentives_fund_institutions,
         -OS_Help_Recognition_promotion_recruitment,
         -OS_Help_Support_seniors,
         -OS_Help_Support_juniors,
         -OS_Help_Positive_beliefs,
         -OS_Help_No_plan_Use_OS,
         -`SS_Definition__slow_process_over_short-term`,
         -`SS_Definition_work-life_balance`,
         -SS_Definition_Changing_metrics,
         -SS_Definition_Increase_research_time,
         -SS_Definition_Diminishing_publications,
         -GS_Relation_research_sustanability)


# head(df)
# names(df)
```

```{r}
#| message: false

library(tidygraph)
library(ggraph)

plot_graph <- function(fa_res, 
                       threshold = 0.3, 
                       loading_text_size = 2.8,
                       arrow_end_gap = 0.10,         
                       factor_node_size = c(22, 35)  
) {
  
  meta_cols <- c("Complexity", "Uniqueness", "MSA", "Mean", "SD")
  
  # 1. Extract ALL loadings first
  df_all <- fa_res |>
    as.data.frame() |>
    data_remove(meta_cols) |>
    data_to_long(
      select = -Variable,
      names_to = "Factor",
      values_to = "Loading"
    )
  
  variables <- unique(df_all$Variable)
  n_var <- length(variables)
  
  original_factors <- unique(df_all$Factor)
  n_fac <- length(original_factors)
  
  # 2. Extract Variance Explained
  # Attempt to extract exact variance from easystats attributes
  var_attr <- attributes(fa_res)$variance
  
  if (!is.null(var_attr)) {
    # Extract the proportion vector
    if (is.numeric(var_attr)) {
      prop_var <- var_attr
    } else if (is.data.frame(var_attr) && "Variance" %in% names(var_attr)) {
      prop_var <- var_attr$Variance
    }
    
    # Ensure names match for safety
    if (is.null(names(prop_var)) && length(prop_var) >= n_fac) {
      names(prop_var) <- original_factors
    }
  } else {
    # Fallback: Recalculate using sum of squared loadings
    ss_loadings <- tapply(df_all$Loading^2, df_all$Factor, sum)
    prop_var <- as.numeric(ss_loadings / n_var)
    names(prop_var) <- names(ss_loadings)
  }
  
  # Saftey check: Some easystats versions return percentages (43.0) instead of proportions (0.43)
  if (max(prop_var, na.rm = TRUE) > 1) {
    prop_var <- prop_var / 100
  }
  
  # 3. Filter by threshold and reshape
  edges <- df_all |>
    subset(abs(Loading) >= threshold) |>
    data_rename(
      pattern = c("Variable", "Factor", "Loading"),
      replacement = c("from", "to", "weight")
    )
  
  # 4. Build a Manual Layout
  y_var <- seq(n_var, 1)
  
  y_fac <- seq(
    from = n_var - 0.5, 
    to = 1.5, 
    length.out = n_fac
  )
  
  nodes <- data.frame(
    name = c(original_factors, variables),
    type = c(rep("Factor", n_fac), rep("Variable", n_var)),
    x = c(rep(1, n_fac), rep(0, n_var)),
    y = c(y_fac, y_var),
    variance = c(prop_var[original_factors], rep(NA, n_var)),
    label_text = c(
      sprintf("%s\n(%.1f%%)", original_factors, prop_var[original_factors] * 100), 
      variables
    )
  )
  
  # 5. Build the tidygraph object
  graph <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
  
  # 6. Plot using ggraph
  ggraph(graph, layout = "manual", x = x, y = y) + 
    
    # -- EDGES --
    geom_edge_link(
      aes(
        edge_width = abs(weight),
        edge_alpha = abs(weight),
        color = weight,
        # Format: Round to 2 decimals, then remove the leading 0
        label = sub("^(-?)0\\.", "\\1.", sprintf("%.2f", weight))
      ),
      arrow = arrow(length = unit(4, 'mm'), type = "closed"),
      
      start_cap = circle(0, 'mm'),    
      
      # Use 'snpc' to make the gap dynamic and relative to the overall plot size
      end_cap = circle(arrow_end_gap, 'snpc'), 
      
      angle_calc = 'along',
      label_dodge = unit(2.5, 'mm'),  
      label_size = loading_text_size
    ) +
    
    # -- FACTOR NODES (Scaled Circles) --
    geom_node_point(
      aes(filter = type == "Factor", size = variance),
      shape = 21,
      fill = "#2C3E50",
      color = "white",
      stroke = 1.5,
      show.legend = FALSE
    ) +
    
    # -- FACTOR TEXT --
    geom_node_text(
      aes(filter = type == "Factor", label = label_text),
      color = "white",
      fontface = "bold",
      size = 3.5,
      lineheight = 0.9 
    ) +
    
    # -- VARIABLE NODES (Boxes) --
    geom_node_label(
      aes(filter = type == "Variable", label = label_text),
      fill = "#95A5A6",
      color = "white",
      fontface = "bold",
      size = 3.5,
      hjust = 1, 
      label.padding = unit(0.5, "lines")
    ) +
    
    # -- SCALES & AESTHETICS --
    scale_size_continuous(range = factor_node_size, guide = "none") +
    
    scale_edge_color_gradient2(
      low = "#E74C3C", mid = "grey85", high = "#2ECC71",
      midpoint = 0, guide = "none" 
    ) +
    scale_edge_width_continuous(range = c(0.5, 2.5), guide = "none") +
    scale_edge_alpha_continuous(range = c(0.4, 1), guide = "none") +
    
    # -- CANVAS EXPANSION & THEME --
    scale_x_continuous(expand = expansion(add = c(0.5, 0.5))) +
    coord_cartesian(clip = "off") + 
    
    theme_graph() +
    theme(
      plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
      plot.margin = margin(20, 20, 20, 20) 
    ) +
    labs(title = "Factor Analysis Loadings")
}
```


## Descriptive

### Demographics

```{r}
gender_colors <- c("Female" = "#E91E63", "Male" = "#1976D2", "Other" = "#4CAF50")

p_age <- df |>
  filter(!is.na(Dem_Age), !is.na(Dem_Gender)) |>
  ggplot(aes(y = after_stat(count), x = Dem_Age, fill = Dem_Gender, color = Dem_Gender)) +
  geom_histogram(aes(y = after_stat(count)), bins = 50, alpha = 0.4, color = NA) +
  geom_density(linewidth = 0.9, alpha = 0) +
  facet_wrap(~Dem_Gender, ncol = 1, scales = "free_y") +
  scale_fill_manual(values = gender_colors, guide = "none") +
  scale_color_manual(values = gender_colors, guide = "none") +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold", size = 11),
        panel.grid.minor = element_blank()) +
  labs(title = "Age Distribution", x = "Age", y = "Count")
p_age
```

```{r}
# Number of children
p_children <- df |>
  filter(!is.na(Dem_Child_numb), Dem_Child_numb != "") |>
  count(Dem_Child_numb) |>
  mutate(Dem_Child_numb = factor(Dem_Child_numb,
    levels = c("I have no children", "1", "2", "3", "More than 3"))) |>
  ggplot(aes(x = Dem_Child_numb, y = n, fill = Dem_Child_numb)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Blues") +
  theme_minimal() +
  labs(title = "Number of Children", x = "", y = "Count")

# Parental leave
leave_levels <- c("Less than 2 weeks", "Between 2 weeks and 1 month",
                  "Between 1 month and 3 months", "Between 3 months and 6 months",
                  "Between 6 months and 1 year", "Between 1 year and 2 years",
                  "More than 2 years", "I did not take any parental leave")
p_parental <- df |>
  filter(!is.na(Dem_Parental_leave), Dem_Parental_leave != "") |>
  count(Dem_Parental_leave) |>
  mutate(Dem_Parental_leave = factor(Dem_Parental_leave, levels = leave_levels)) |>
  ggplot(aes(x = Dem_Parental_leave, y = n, fill = Dem_Parental_leave)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Greens") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Parental Leave", x = "", y = "Count")

p_children + p_parental
```

```{r}
# Research discipline — pie chart
p_discipline <- df |>
  filter(!is.na(Work_Discipline), Work_Discipline != "") |>
  count(Work_Discipline) |>
  mutate(pct = n / sum(n),
         label = paste0(Work_Discipline, "\n", n, " (", round(pct * 100), "%)")) |>
  ggplot(aes(x = "", y = n, fill = Work_Discipline)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") +
  geom_text(aes(label = label), position = position_stack(vjust = 0.5),
            size = 3.5, color = "white", fontface = "bold") +
  scale_fill_brewer(palette = "Set2") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Research Discipline")

# Highest diploma
p_diploma <- df |>
  filter(!is.na(Work_Diploma), Work_Diploma != "") |>
  count(Work_Diploma) |>
  mutate(Work_Diploma = factor(Work_Diploma,
    levels = c("Bachelor", "Master", "PhD", "Other"))) |>
  ggplot(aes(x = Work_Diploma, y = n, fill = Work_Diploma)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Purples") +
  theme_minimal() +
  labs(title = "Highest Diploma", x = "", y = "Count")

p_discipline + p_diploma
```

```{r}
# Academic position
p_position <- df |>
  filter(!is.na(Work_Position), Work_Position != "") |>
  count(Work_Position) |>
  ggplot(aes(x = reorder(Work_Position, n), y = n, fill = n)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = n), hjust = -0.2, size = 3, color = "grey30") +
  scale_fill_gradient(low = "#b3cde3", high = "#084594") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  labs(title = "Academic Position", x = "", y = "Count")

# Country of work + specific affiliations (dodged)
clean_country <- function(x) {
  x <- str_to_title(str_trim(x))
  case_when(
    x %in% c("Uk", "United Kingdom", "England", "Wales (Uk)", "Uk - England") ~ "United Kingdom",
    x %in% c("Be", "Belgique", "Belgium") ~ "Belgium",
    x %in% c("Nl", "The Netherlands") ~ "Netherlands",
    x %in% c("Usa", "United States") ~ "United States",
    x %in% c("Italia") ~ "Italy",
    x %in% c("Suisse") ~ "Switzerland",
    x %in% c("Feance", "Frabce", "France ", "France/Canada",
             "Germany And France", "Dijon", "Grenoble") ~ "France",
    .default = x
  )
}

normalize_affil <- function(x) {
  x <- str_trim(x)
  case_when(
    x == "" | is.na(x)                                                              ~ "Missing",
    str_detect(x, regex("^cnrs", ignore_case = TRUE))                               ~ "CNRS",
    str_detect(x, regex("^inserm", ignore_case = TRUE))                             ~ "INSERM",
    str_detect(x, regex("^inrae", ignore_case = TRUE))                              ~ "INRAE",
    str_detect(x, regex("^cea$", ignore_case = TRUE))                               ~ "CEA",
    str_detect(x, regex("^ens$", ignore_case = TRUE))                               ~ "ENS",
    str_detect(x, regex("^ucl$", ignore_case = TRUE))                               ~ "UCL",
    str_detect(x, regex("sorbonne univ|^sorbonne universit", ignore_case = TRUE))   ~ "Sorbonne Univ.",
    str_detect(x, regex("paris cit|upcit", ignore_case = TRUE))                     ~ "Univ. Paris Cité",
    str_detect(x, regex("sussex", ignore_case = TRUE))                              ~ "Univ. of Sussex",
    str_detect(x, regex("^ghent|universiteit gent", ignore_case = TRUE))            ~ "Ghent University",
    str_detect(x, regex("eth zurich|eth zürich|^eth$", ignore_case = TRUE))         ~ "ETH Zurich",
    str_detect(x, regex("^psl$|psl research|psl univ", ignore_case = TRUE))         ~ "PSL",
    str_detect(x, regex("toulouse", ignore_case = TRUE))                            ~ "Univ. de Toulouse",
    str_detect(x, regex("lille", ignore_case = TRUE))                               ~ "Univ. de Lille",
    str_detect(x, regex("grenoble", ignore_case = TRUE))                            ~ "Univ. Grenoble Alpes",
    str_detect(x, regex("bordeaux", ignore_case = TRUE))                            ~ "Univ. de Bordeaux",
    str_detect(x, regex("lyon", ignore_case = TRUE))                                ~ "Univ. de Lyon",
    str_detect(x, regex("strasbourg", ignore_case = TRUE))                          ~ "Univ. de Strasbourg",
    str_detect(x, regex("aix.marseille|aix marseille", ignore_case = TRUE))         ~ "Aix-Marseille Univ.",
    str_detect(x, regex("^bcbl$|basque center on cognition", ignore_case = TRUE))   ~ "BCBL",
    str_detect(x, regex("clermont", ignore_case = TRUE))                            ~ "Univ. Clermont",
    str_detect(x, regex("montpellier", ignore_case = TRUE))                         ~ "Univ. de Montpellier",
    str_detect(x, regex("paris.saclay|paris saclay", ignore_case = TRUE))           ~ "Univ. Paris-Saclay",
    str_detect(x, regex("paris 8", ignore_case = TRUE))                             ~ "Univ. Paris 8",
    str_detect(x, regex("^ulb$|ulb,|libre de bruxelles", ignore_case = TRUE))       ~ "ULB",
    str_detect(x, regex("leiden", ignore_case = TRUE))                              ~ "Leiden University",
    str_detect(x, regex("picardie", ignore_case = TRUE))                            ~ "Univ. Picardie",
    str_detect(x, regex("côte d.azur|cote d.azur", ignore_case = TRUE))             ~ "Univ. Côte d'Azur",
    str_detect(x, regex("rennes", ignore_case = TRUE))                              ~ "Univ. de Rennes",
    str_detect(x, regex("groningen", ignore_case = TRUE))                           ~ "Univ. of Groningen",
    str_detect(x, regex("caen", ignore_case = TRUE))                                ~ "Univ. de Caen",
    str_detect(x, regex("minho", ignore_case = TRUE))                               ~ "Univ. of Minho",
    str_detect(x, regex("turin", ignore_case = TRUE))                               ~ "Univ. of Turin",
    .default = x
  )
}

# Include ALL rows; normalize_affil returns "Missing" for empty/NA
df_country_aff_all <- df |>
  filter(!is.na(Work_Country), Work_Country != "") |>
  mutate(
    Country = clean_country(Work_Country),
    Affiliation = normalize_affil(Work_Affiliation)
  )

country_palette_ext <- c(
  "France"         = "#1976D2",
  "United Kingdom" = "#E91E63",
  "Germany"        = "#FF9800",
  "Spain"          = "#8BC34A",
  "Belgium"        = "#9C27B0",
  "Italy"          = "#00BCD4",
  "Netherlands"    = "#F44336",
  "Switzerland"    = "#795548",
  "United States"  = "#607D8B",
  "Other country"  = "#C8E6C9",
  "—"              = "#BDBDBD"   # for Missing / Other affiliation buckets
)

# Named affiliations = those with n >= 3 after normalisation
named_affils <- df_country_aff_all |>
  filter(Affiliation != "Missing") |>
  count(Affiliation, sort = TRUE) |>
  filter(n >= 2) |>
  pull(Affiliation)

df_plot_affil <- df_country_aff_all |>
  mutate(
    Affiliation_cat = case_when(
      Affiliation == "Missing"          ~ "Missing",
      Affiliation %in% named_affils     ~ Affiliation,
      .default                          = "Other"
    ),
    Country_fill = case_when(
      Affiliation_cat %in% c("Missing", "Other") ~ "—",
      Country %in% names(country_palette_ext)     ~ Country,
      .default                                     = "Other country"
    )
  ) |>
  count(Affiliation_cat, Country_fill)

# Order: by total count, with Other/Missing pinned at the bottom
affil_totals <- df_plot_affil |>
  group_by(Affiliation_cat) |>
  summarise(total = sum(n), .groups = "drop") |>
  mutate(rank = case_when(
    Affiliation_cat == "Missing" ~ -2L,
    Affiliation_cat == "Other"   ~ -1L,
    .default = as.integer(total)
  )) |>
  arrange(rank)

affil_level_order <- affil_totals$Affiliation_cat

affil_label_df <- affil_totals |>
  mutate(Affiliation_cat = factor(Affiliation_cat, levels = rev(affil_level_order)))

p_country <- df_plot_affil |>
  mutate(Affiliation_cat = factor(Affiliation_cat, levels = affil_level_order)) |>
  ggplot(aes(x = Affiliation_cat, y = n, fill = Country_fill)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(data = affil_label_df,
            aes(x = Affiliation_cat, y = total, label = total),
            inherit.aes = FALSE,
            hjust = -0.2, size = 3, color = "grey30") +
  scale_fill_manual(values = country_palette_ext, name = "Country") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "right",
        legend.text = element_text(size = 7.5),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y = element_text(size = 8)) +
  labs(title = "Affiliations by Country of Work (n ≥ 3; others grouped)",
       x = "", y = "Count")

p_position + p_country
```

```{r}
# Time allocation across research activities
p_activities <- df |>
  select(Work_Time_Research, Work_Time_Teaching, Work_Time_Administration,
         Work_Time_Popularization, Work_Time_Other) |>
  rename(Research = Work_Time_Research,
         Teaching = Work_Time_Teaching,
         Administration = Work_Time_Administration,
         Popularization = Work_Time_Popularization,
         Other = Work_Time_Other) |>
  pivot_longer(everything(), names_to = "Activity", values_to = "Percentage") |>
  filter(!is.na(Percentage)) |>
  mutate(Activity = factor(Activity,
    levels = c("Research", "Teaching", "Administration", "Popularization", "Other")),
    Percentage = Percentage / 100) |>
  ggplot(aes(x = Activity, y = Percentage, fill = Activity)) +
  geom_violin(alpha = 0.6, trim = TRUE) +
  geom_boxplot(width = 0.1, fill = "white", outlier.size = 0.5) +
  scale_fill_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Time Allocation Across Activities", x = "", y = "Proportion of Work Time")
p_activities
```

```{r}
# Career perceptions: scatterplot matrix with ggside marginals
pub_colors <- c("Yes" = "#1976D2", "No" = "#E91E63")

df_career <- df |>
  filter(!is.na(Work_Publication)) |>
  transmute(
    Published = Work_Publication,
    Prob_Perm = Work_Probability_permanent_position / 100,
    Sat_Numb  = Work_Satisfaction_numb_publications  / 100,
    Sat_Qual  = Work_Satisfaction_quality_publications / 100
  )

make_scatter_side <- function(data, xv, yv, xl, yl) {
  ggplot(data |> filter(!is.na(.data[[xv]]), !is.na(.data[[yv]])),
         aes(x = .data[[xv]], y = .data[[yv]])) +
    geom_point(alpha = 0.3, size = 2, color = "#1976D2") +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.12, linewidth = 0.8,
                color = "#1976D2", fill = "#1976D2") +
    geom_xsidehistogram(bins = 15, alpha = 0.5, fill = "#1976D2") +
    geom_ysidehistogram(bins = 15, alpha = 0.5, fill = "#1976D2") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_bw() +
    theme(ggside.panel.scale = 0.25,
          ggside.panel.border = element_blank(),
          ggside.panel.background = element_blank(),
          ggside.axis.ticks.x = element_blank(),
          ggside.axis.ticks.y = element_blank()) +
    labs(x = xl, y = yl)
}

p_ab <- make_scatter_side(df_career, "Prob_Perm", "Sat_Numb",
                          "P(Permanent Position)", "Sat. No. Publications")
p_ac <- make_scatter_side(df_career, "Prob_Perm", "Sat_Qual",
                          "P(Permanent Position)", "Sat. Quality Publications")
p_bc <- make_scatter_side(df_career, "Sat_Numb", "Sat_Qual",
                          "Sat. No. Publications", "Sat. Quality Publications")

p_pub_bar <- df |>
  filter(!is.na(Work_Publication), Work_Publication != "") |>
  count(Work_Publication) |>
  ggplot(aes(x = Work_Publication, y = n, fill = Work_Publication)) +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
  scale_fill_manual(values = pub_colors) +
  theme_bw() +
  labs(title = "Has Published?", x = "", y = "Count")

(p_ab | p_ac) / (p_bc | p_pub_bar) +
  plot_annotation(
    title = "Career Perceptions — Pairwise Relationships",
    theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5))
  )
```

```{r}
# Committee/service involvement and clinical activity
p_commit <- df |>
  filter(!is.na(Work_Committees), Work_Committees != "") |>
  count(Work_Committees) |>
  ggplot(aes(x = Work_Committees, y = n, fill = Work_Committees)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("Yes" = "#4dac26", "No" = "#d01c8b")) +
  theme_minimal() +
  labs(title = "Member of Committees", x = "", y = "Count")

p_clinical <- df |>
  filter(!is.na(Work_Clinical_activity), Work_Clinical_activity != "") |>
  count(Work_Clinical_activity) |>
  ggplot(aes(x = Work_Clinical_activity, y = n, fill = Work_Clinical_activity)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("Yes" = "#4dac26", "No" = "#d01c8b")) +
  theme_minimal() +
  labs(title = "Clinical Activity", x = "", y = "Count")

# Quality criteria importance (binary endorsement rates)
df |>
  select(starts_with("Work_Criteria_quality_science_")) |>
  rename_with(~str_remove(., "Work_Criteria_quality_science_")) |>
  pivot_longer(everything(), names_to = "Criterion", values_to = "Endorsed") |>
  filter(!is.na(Endorsed)) |>
  group_by(Criterion) |>
  summarise(pct = mean(Endorsed == "Yes"), .groups = "drop") |>
  ggplot(aes(x = reorder(Criterion, pct), y = pct, fill = pct)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(low = "#fee8c8", high = "#b30000", guide = "none") +
  scale_y_continuous(labels = scales::percent_format()) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Endorsement of Quality Criteria for Science",
       x = "", y = "% endorsing") ->
  p_criteria

(p_commit + p_clinical) / p_criteria
```

### Open Science Practices

#### Overview

```{r}
df_os_practices <- select(df, starts_with("OS_"), -starts_with("OS_Help")) 

p_os_prac1 <- correlation(df_os_practices, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Cooccurence of Open Science Practices",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_os_prac1

rez <- n_factors(df_os_practices)
plot(rez)

f <- factor_analysis(df_os_practices, n=3)
plot(f)
p_os_prac2 <- plot_graph(f, threshold = 0.2, arrow_end_gap = 0.12)
p_os_prac2

df <- get_scores(f) |>
  data_rename(replacement = c("OS_Subjective", "OS_Rigour", "OS_Transparency")) |>
  cbind(df)
df$OS_General <- rowMeans(df[c("OS_Subjective", "OS_Rigour", "OS_Transparency")], na.rm = TRUE)
```

#### Predictors

```{r}
m_osgen <- brms::brm(OS_General ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male")),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")

m_osrig <- brms::brm(OS_Rigour ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male")),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")

m_ostra <- brms::brm(OS_Transparency ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male")),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")

m_ossub <- brms::brm(OS_Subjective ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male")),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")


p_os_pred1 <- rbind(
  mutate(estimate_relation(m_osgen, length = 40), Outcome = "Open Science - General"),
  mutate(estimate_relation(m_osrig, length = 40), Outcome = "Open Science - Rigour"),
  mutate(estimate_relation(m_ostra, length = 40), Outcome = "Open Science - Transparency"),
  mutate(estimate_relation(m_ossub, length = 40), Outcome = "Open Science - Subjective")
) |>
  ggplot(aes(x = Dem_Age, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Outcome, 
                  group = interaction(Dem_Gender, Outcome)), alpha = 0.1) +
  geom_line(aes(color=Outcome, linetype = Dem_Gender, linewidth = Outcome)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  scale_colour_manual(values = c("Open Science - General" = "#212121", "Open Science - Rigour" = "#9C27B0", "Open Science - Transparency" = "#3F51B5", "Open Science - Subjective" = "#2196F3")) +
  scale_fill_manual(values = c("Open Science - General" = "#212121", "Open Science - Rigour" = "#9C27B0", "Open Science - Transparency" = "#3F51B5", "Open Science - Subjective" = "#2196F3")) +
  scale_linewidth_manual(values = c("Open Science - General" = 1.2, "Open Science - Rigour" = 0.8, "Open Science - Transparency" = 0.8, "Open Science - Subjective" = 0.8)) +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Score", x = "Age",
       fill = "Outcome", color = "Outcome", linetype = "Gender",
       title = "Gender and Age") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_os_pred1
```


### Open Science Help

```{r}
df_os_help <- select(df, starts_with("OS_Help"), -OS_Help_Other)
names(df_os_help) <- str_replace(names(df_os_help), "OS_Help_", "") |>
  str_replace_all(fixed("_"), " ")

correlation(df_os_help, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Open Science Help Avenues",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p_os_help <- df_os_help |>
  mutate(participant = paste0("S", 1:nrow(df_os_help))) |>
  pivot_longer(-participant) |>
  summarize(Total = sum(value) / nrow(df_os_help), .by="name") |>
  mutate(Type = case_when(name %in% c("Recognition Promotion Recruitment") ~ "Recognition", name %in% c("Incentives Fund Institutions", "Funding") ~ "Money", name %in% c("Time", "Workload") ~ "Time", name %in% c("Infrastructure", "Support Seniors", "Training", "Support Juniors") ~ "Support", .default = "Other"),
         Type = fct_relevel(Type, "Recognition", "Money", "Time", "Support"),
         name = case_when(str_detect(name, "Recognition") ~ "Recognition (Recruitment/Promotion)", .default = name),
         name =  fct_reorder(name, desc(Total)),) |>
  ggplot(aes(x = name, y = Total, fill = Type)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Recognition" = "#E91E63", "Money" = "gold", "Time" = "#4CAF50", "Support" = "#1E88E5", "Other" = "grey")) +
  theme_minimal() +
  labs(title = "What would you need to further adopt open science practices?",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_os_help
```


### Slow Science

```{r}
df_ss_scales <- select(df, SS_Familiar, SS_Importance, SS_Workshops)

correlation(df_ss_scales, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Slow Science Scales",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Slow Science Definition

```{r}
df_ss_def <- select(df, starts_with("SS_Definition_"), -SS_Definition_Other)
names(df_ss_def) <- str_replace(names(df_ss_def), "SS_Definition_", "") |>
  str_replace_all(fixed("_"), " ")

ss_def <- df_ss_def |>
  mutate(participant = paste0("S", 1:nrow(df_ss_def))) |>
  pivot_longer(-participant) |>
  summarize(Total = sum(value, na.rm = TRUE) / nrow(df_ss_def), .by = "name") |>
  mutate(name = fct_reorder(name, desc(Total))) |>
  ggplot(aes(x = name, y = Total, fill=Total)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_gradient(low = "lightblue", high = "steelblue", guide = "none") +
  theme_minimal() +
  labs(title = "Which of these best describes Slow Science for you?",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
ss_def
```

### Slow Science Feasibility

```{r}
ss_feas <- select(df, matches("^SS_.*Feasible_individual$|^SS_.*Feasible_institution$|^SS_.*Not_Feasible$")) |>
  mutate(participant = paste0("S", seq_len(n()))) |>
  pivot_longer(-participant, names_to = "Variable", values_to = "value") |>
  mutate(
    Practice = Variable |>
      str_remove("^SS_") |>
      str_remove("_Feasible_individual$|_Feasible_institution$|_Not_Feasible$") |>
      str_replace_all("_", " "),
    Level = case_when(
      str_detect(Variable, "_Feasible_individual$") ~ "Individual",
      str_detect(Variable, "_Feasible_institution$") ~ "Institution",
      str_detect(Variable, "_Not_Feasible$") ~ "Not Feasible"
    ),
    Level = fct_relevel(Level, "Individual", "Institution", "Not Feasible")
  ) |>
  summarize(Proportion = sum(value, na.rm = TRUE) / n_distinct(participant),
            .by = c(Practice, Level)) |> 
  mutate(Practice = fct_reorder(Practice, ifelse(Level == "Institution", Proportion, 0), .fun = \(x) sum(x, na.rm = TRUE), .desc = TRUE)) |>
  ggplot(aes(x = Practice, y = Proportion, fill = Level)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Individual" = "#4CAF50", "Institution" = "#1E88E5", "Not Feasible" = "#E53935")) +
  theme_minimal() +
  labs(title = "Who Can Help Slow Science Practices?",
       x = "", y = "", fill = NULL) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
ss_feas
```

### Green Science

```{r}
df_gs <- select(df, starts_with("GS_"))

correlation(df_gs, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Green Science Scales",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

rez_gs <- n_factors(df_gs)
plot(rez_gs)

f <- factor_analysis(df_gs, n=2)
plot(f)

df <- get_scores(f) |>
  data_rename(replacement = c("GS_Importance", "GS_Action")) |>
  cbind(df)
```

### Ethical Science

```{r}
df_es <- select(df, starts_with("ES_"))

correlation(df_es, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Ethical Science Scales",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Archetypes of Agathic Science

Alternative names:
- Agathic Science
- Honest Science
- New Science

```{r}
# OS_General = composite of actual practice scores (subjective familiarity + importance captured by OS_Familiar)
# GS_Change_practices_agreeing replaces GS_Importance_topic (less redundant with GS_Importance_conducting)
cluster_vars <- c(
  "OS_Familiar", "OS_Importance", "OS_Rigour", "OS_Transparency",
  "SS_Familiar", "SS_Importance",
  "GS_Importance", "GS_Action",
  "ES_Importance_research_team", "ES_Consequences_society"     # ES: two facets
)
# Short axis labels for the radar — must match cluster_vars exactly
labels <- tibble(
  Variable = cluster_vars,
  label = c(
    "Open Science\nFamiliarity",
    "Open Science\nImportance",
    "Open Science\nRigour",
    "Open Science\nTransparency",
    "Slow Science\nFamiliarity",
    "Slow Science\nImportance",
    "Green Science\nImportance",
    "Green Science\nAction",
    "EDI Science\nTeam",
    "EDI Science\nSociety"
  )
)


data <- select(df, all_of(cluster_vars))

p_cor <- data |>
  data_rename(replacement = str_replace_all(labels$label, "\n", " - ")) |>
  correlation(redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Research Values",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_cor
```

```{r}
n_clusters(data) |>
  plot()

rez <- cluster_analysis(data, n=4, method="hkmeans")
plot(rez)
df$Profile <- predict(rez)
df <- mutate(df, Profile = case_when(
           Profile == 1 ~ "Cluster 1 - Idealists",
           Profile == 2 ~ "Cluster 2 - Ethical Productivists",
           Profile == 3 ~ "Cluster 3 - Openness Champions",
           .default = "Cluster 4 - Ethical Radicalists"
         ))
```

```{r}
n_vars  <- length(cluster_vars)
angles  <- seq(0, 2 * pi, length.out = n_vars + 1)[seq_len(n_vars)]

# Cluster means, normalised to [0,1] using full-data range per variable
var_mins <- sapply(cluster_vars, \(v) min(df[[v]], na.rm = TRUE))
var_maxs <- sapply(cluster_vars, \(v) max(df[[v]], na.rm = TRUE))

radar_means <- df |>
  group_by(Profile) |>
  summarise(across(all_of(cluster_vars), \(x) mean(x, na.rm = TRUE)), .groups = "drop")

for (v in cluster_vars) {
  radar_means[[v]] <- (radar_means[[v]] - var_mins[v]) / (var_maxs[v] - var_mins[v])
}

# Long format with (x, y) cartesian coords
radar_long <- radar_means |>
  pivot_longer(-Profile, names_to = "Variable", values_to = "r") |>
  left_join(tibble(Variable = cluster_vars, angle = angles), by = "Variable") |>
  mutate(x = r * sin(angle), y = r * cos(angle))

# Close each polygon by appending the first point again
radar_closed <- radar_long |>
  group_by(Profile) |>
  group_modify(\(d, .y) bind_rows(d, d[1, ])) |>
  ungroup()

# Background grid (concentric circles + spokes)
grid_circles <- expand.grid(r = c(.25, .5, .75, 1), theta = seq(0, 2 * pi, length.out = 200)) |>
  mutate(x = r * sin(theta), y = r * cos(theta), r = factor(r))

spokes <- tibble(Variable = cluster_vars, angle = angles) |>
  mutate(x1 = sin(angle), y1 = cos(angle))

# Use left_join instead of named-vector indexing to avoid NA from tibble column lookup
axis_labels <- spokes |>
  left_join(labels, by = "Variable") |>
  mutate(lx = 1.25 * sin(angle), ly = 1.25 * cos(angle))

p_radar <- ggplot() +
  # Grid circles
  geom_path(data = grid_circles, aes(x = x, y = y, group = r),
            colour = "grey85", linewidth = 0.3) +
  # Grid labels
  geom_text(data = tibble(r = c(.25, .5, .75, 1)),
            aes(x = 0.02, y = r, label = r), size = 2.2, colour = "grey60", hjust = 0) +
  # Spokes
  geom_segment(data = spokes, aes(x = 0, y = 0, xend = x1, yend = y1),
               colour = "grey75", linewidth = 0.4) +
  # Axis labels
  geom_text(data = axis_labels, aes(x = lx, y = ly, label = label),
            size = 3, lineheight = 0.85, fontface = "bold") +
  # Cluster polygons
  geom_polygon(data = radar_closed, aes(x = x, y = y, colour = Profile, fill = Profile, group = Profile),
               alpha = 0.15, linewidth = 0.9) +
  geom_point(data = radar_long, aes(x = x, y = y, colour = Profile), size = 2.5) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  coord_equal(xlim = c(-1.6, 1.6), ylim = c(-1.6, 1.6)) +
  theme_void() +
  theme(plot.margin = margin(10, 10, 10, 10),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5)) +
  labs(title = "Researcher Profiles by Cluster", colour = NULL, fill = NULL)

p_radar
```

### Predictors

```{r}
m <- brms::brm(Profile ~ Dem_Gender * poly(Dem_Age, 2), 
               family = brms::categorical(), 
               data = df |> 
                 mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                 filter(Dem_Gender %in% c("Female", "Male")),
               backend = "cmdstanr",
               algorithm = "pathfinder")

p_archetypes_pred1 <- estimate_relation(m, length = 40) |> 
  ggplot(aes(x = Dem_Age, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Response, 
                  group = interaction(Dem_Gender, Response)), alpha = 0.1) +
  geom_line(aes(color=Response, linetype = Dem_Gender), linewidth = 1) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Probability of Belonging to Each Archetype", x = "Age",
       fill = "Archetype", color = "Archetype", linetype = "Gender",
       title = "Proportion of Profiles as a function of Gender and Age") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_archetypes_pred1
```


## Figures

### Demographics

```{r}
#| fig-width: 12
#| fig-height: 30
#| warning: false

p_age / 
  (p_children + p_parental) / 
  (p_discipline + p_diploma) / 
  p_activities /
  patchwork::wrap_elements(p_position + p_country)

# (p_position | p_country) / (p_time | p_career) +
#   plot_layout(heights = c(0.5, 0.5)) +
#   plot_annotation(title = "Demographics", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```


### Open Science

```{r}
#| fig-width: 12
#| fig-height: 12
#| warning: false

(p_os_prac2 | p_os_prac1) / p_os_help + 
  plot_layout(heights = c(0.6, 0.4)) +
  plot_annotation(title = "Open Science Adoption", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```

```{r}
#| fig-width: 12
#| fig-height: 6
#| warning: false

p_os_pred1 +
  plot_annotation(title = "Predictors of Open Science Practices", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```


### Slow Science

```{r}
#| fig-width: 8
#| fig-height: 10
#| warning: false

ss_def / ss_feas  +
  plot_annotation(title = "Slow Science", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```

### Archetypes of Ethical Science

```{r}
#| fig-width: 16
#| fig-height: 12
#| warning: false

(p_cor + p_radar + 
  plot_layout(widths = c(0.4, 0.6))) / p_archetypes_pred1 +
  plot_annotation(title = "Archetypes of Ethical Science", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```

