---
title: "MapResPrac - Data Cleaning"
editor: source
editor_options:
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r init}
#| warning: false
#| code-fold: true
#| error: false
#| message: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)

question_labels <- readxl::read_xlsx("MapResPrac_correspondance.xlsx")
# names(question_labels)  # Question long names

df <- read.csv("MapResPrac-080426-557.csv")
names(df) <- as.character(as.vector(question_labels[1,])) |>
  str_replace_all(fixed(".  "), "_") |>
  str_replace_all(fixed(". "), "_") |>
  str_replace_all(fixed("."), "_") |>
  str_replace_all(fixed(" "), "_") |>
  str_replace_all(fixed("/"), "_")

format_binary <- function(x) {
  case_when(x == "Yes" ~ 1, x == "No" ~ 0, .default = NA)
}
format_use <- function(x) {
  case_when(x == "I know it and I used it" ~ 3/3,
            x == "I haven't used it yet, but I plan to do it in the future" ~ 2/3,
            x == "I am not familiar with it" ~ 1/3,
            x == "I haven't used it yet, and I don't plan to do it in the future" ~ 0,
            .default = NA)
}


df <- df |>
  select(-contains(" time: ")) |>
  mutate(Dem_Gender = ifelse(Dem_Gender == "Non-binary", "Other", Dem_Gender),
         Dem_Age = ifelse(Dem_Age < 18, NA, Dem_Age),
         OS_Familiar = OS_Familiar / 100,
         OS_Importance = OS_Importance / 100,
         OS_Workshops = format_binary(OS_Workshops),
         OS_Study_Preregistration = format_use(OS_Study_Preregistration),
         OS_Registered_Reports = format_use(OS_Registered_Reports),
         OS_Open_Materials = format_use(OS_Open_Materials),
         OS_Open_Data = format_use(OS_Open_Data),
         OS_Open_Peer_Review = format_use(OS_Open_Peer_Review),
         OS_Open_Access_Publication = format_use(OS_Open_Access_Publication),
         OS_Replication_Studies = format_use(OS_Replication_Studies),
         OS_Participatory_Research = format_use(OS_Participatory_Research),
         OS_Help_More_Information = format_binary(OS_Help_More_information),
         OS_Help_Training = format_binary(OS_Help__training),
         OS_Help_Ethical_Issues = format_binary(OS_Help_ethical_issues),
         OS_Help_Infrastructure = format_binary(OS_Help_infrastructure),
         OS_Help_Time = format_binary(OS_Help_time),
         OS_Help_Workload = format_binary(OS_Help_Workload),
         OS_Help_Funding = format_binary(OS_Help_Funding),
         OS_Help_Incentives_Fund_Institutions = format_binary(OS_Help_Incentives_fund_institutions),
         OS_Help_Recognition_Promotion_Recruitment = format_binary(OS_Help_Recognition_promotion_recruitment),
         OS_Help_Support_Seniors = format_binary(OS_Help_Support_seniors),
         OS_Help_Support_Juniors = format_binary(OS_Help_Support_juniors),
         OS_Help_Positive_Beliefs = format_binary(OS_Help_Positive_beliefs),
         OS_Help_No_Plan_Use_OS = format_binary(OS_Help_No_plan_Use_OS),
         OS_Help_Nothing = format_binary(OS_Help_Nothing),
         # Slow Science
         SS_Familiar = SS_Familiar / 100,
         SS_Importance = SS_Importance / 100,
         SS_Workshops = format_binary(SS_Workshops),
         SS_Definition_Quality_over_quantity = format_binary(SS_Definition_Quality_over_quantity),
         SS_Definition_Slow_Process = format_binary(`SS_Definition__slow_process_over_short-term`),
         SS_Definition_Changing_Metrics = format_binary(SS_Definition_Changing_metrics),
         SS_Definition_Increase_Research_Time = format_binary(SS_Definition_Increase_research_time),
         SS_Definition_Diminishing_Publications = format_binary(SS_Definition_Diminishing_publications),
         SS_Definition_Work_Life_Balance = format_binary(`SS_Definition_work-life_balance`),
         across(starts_with("SS_") & matches("Feasible|Not_Feasible"), ~replace_na(.x, 0)),
         # Green Science
         GS_Importance_conducting = GS_Importance_conducting / 100,
         GS_Importance_topic = GS_Importance_topic / 100,
         GS_Changes_practices = GS_Changes_practices / 100,
         GS_Changes_communication_practices = GS_Changes_communication_practices / 100,
         GS_Relation_Research_Sustainability = GS_Relation_research_sustanability / 100,
         GS_Change_practices_agreeing = GS_Change_practices_agreeing / 100,
         # Ethical Science
         ES_Importance_research_team = ES_Importance_research_team / 100,
         ES_Consequences_society = ES_Consequences_society / 100,
         # Well-being (0-100 sliders → 0-1)
         WB_Fulfilled              = WB_Fulfilled / 100,
         WB_Alignment              = WB_Alignment / 100,
         WB_Time_research          = WB_Time_research / 100,
         WB_Satisfaction_work_personal = WB_Satisfaction_work_personal / 100,
         WB_Carrer_worry           = WB_Carrer_worry / 100,
         # Career stage (ordered: PhD/Student < Non-permanent < Permanent)
         Work_Career_Stage = fct_relevel(case_when(
           Work_Position %in% c("Master student/Research assistant",
                                "PhD candidate (scholarship, other funding)") ~ "PhD / Student",
           Work_Position %in% c("Postdoc (fixed term)",
                                "Researcher/lecturer (fixed term)",
                                "Engineer (fixed term)")                      ~ "Non-permanent",
           Work_Position == "Permanent position"                              ~ "Permanent",
           .default = NA_character_
         ), "PhD / Student", "Non-permanent", "Permanent"),
         # Does the researcher value impact-factor journals as a quality criterion?
         Work_IF_Values = as.numeric(`Work_Criteria_quality_science_high-IF` == "Yes"),
         Work_Time_Research = Work_Time_Research / 100,
         Work_Satisfaction_numb_publications = Work_Satisfaction_numb_publications / 100
         ) |>
  select(-OS_Help__training,
         -OS_Help_More_information,
         -OS_Help_ethical_issues,
         -OS_Help_infrastructure,
         -OS_Help_time,
         -OS_Help_Incentives_fund_institutions,
         -OS_Help_Recognition_promotion_recruitment,
         -OS_Help_Support_seniors,
         -OS_Help_Support_juniors,
         -OS_Help_Positive_beliefs,
         -OS_Help_No_plan_Use_OS,
         -`SS_Definition__slow_process_over_short-term`,
         -`SS_Definition_work-life_balance`,
         -SS_Definition_Changing_metrics,
         -SS_Definition_Increase_research_time,
         -SS_Definition_Diminishing_publications,
         -GS_Relation_research_sustanability)


# head(df)
# names(df)
```

```{r}
#| message: false
# Load the required packages
library(parameters)
library(datawizard) 
library(tidygraph)
library(ggraph)
library(ggplot2)

plot_graph <- function(fa_res, 
                       threshold = 0.3, 
                       loading_text_size = 2.8,
                       arrow_end_gap = 0.10,         
                       factor_node_size = c(22, 35),
                       expand = c(0.5, 0.5),
                       names_factors = NULL,
                       color_variables = "#95A5A6",
                       color_factors = "#2C3E50"
) {
  
  meta_cols <- c("Complexity", "Uniqueness", "MSA", "Mean", "SD")
  
  # Helper function to process colors and reorder nodes
  process_colors_and_order <- function(items, color_input, default_color) {
    if (is.null(color_input)) {
      return(list(items = items, colors = rep(default_color, length(items))))
    }
    
    if (is.list(color_input)) color_input <- unlist(color_input)
    
    # 1. Handle named list/vector (e.g., c("Var3" = "red", "Var1" = "blue"))
    if (!is.null(names(color_input))) {
      input_names <- names(color_input)
      
      # Match against existing nodes
      valid_names <- input_names[input_names %in% items]
      missing_items <- setdiff(items, valid_names)
      
      # Reorder: Listed items first, missing items follow
      ordered_items <- c(valid_names, missing_items)
      
      # Assign colors based on new order
      mapped_colors <- color_input[ordered_items]
      mapped_colors[is.na(mapped_colors)] <- default_color # Fallback for missing
      
      return(list(items = ordered_items, colors = unname(mapped_colors)))
    }
    
    # 2. Handle single color value
    if (length(color_input) == 1) {
      return(list(items = items, colors = rep(color_input, length(items))))
    }
    
    # 3. Handle unnamed vector of matching length
    if (length(color_input) == length(items)) {
      return(list(items = items, colors = color_input))
    }
    
    # Fallback
    warning("Color vector length does not match number of nodes. Using default color.")
    return(list(items = items, colors = rep(default_color, length(items))))
  }
  
  
  # 1. Extract ALL loadings first
  df_all <- fa_res |>
    as.data.frame() |>
    data_remove(meta_cols) |>
    data_to_long(
      select = -Variable,
      names_to = "Factor",
      values_to = "Loading"
    )
  
  # Process Variables (Color & Order)
  var_processed <- process_colors_and_order(unique(df_all$Variable), color_variables, "#95A5A6")
  variables <- var_processed$items
  var_colors <- var_processed$colors
  n_var <- length(variables)
  
  # Process Factors (Color & Order)
  fac_processed <- process_colors_and_order(unique(df_all$Factor), color_factors, "#2C3E50")
  original_factors <- fac_processed$items
  fac_colors <- fac_processed$colors
  n_fac <- length(original_factors)
  
  # Process Custom Factor Names for Labels
  display_factors <- original_factors
  
  if (!is.null(names_factors)) {
    if (!is.null(names(names_factors))) {
      if (any(unlist(names_factors) %in% original_factors)) {
        lookup <- setNames(names(names_factors), unlist(names_factors))
      } else {
        lookup <- setNames(unlist(names_factors), names(names_factors))
      }
      matched <- original_factors %in% names(lookup)
      display_factors[matched] <- lookup[original_factors[matched]]
      
    } else if (length(names_factors) == n_fac) {
      display_factors <- unlist(names_factors)
    } else {
      warning("`names_factors` must be named, or match the exact number of factors. Ignoring custom names.")
    }
  }
  
  # 2. Extract Variance Explained
  var_attr <- attributes(fa_res)$variance
  
  if (!is.null(var_attr)) {
    if (is.numeric(var_attr)) {
      prop_var <- var_attr
    } else if (is.data.frame(var_attr) && "Variance" %in% names(var_attr)) {
      prop_var <- var_attr$Variance
    }
    
    if (is.null(names(prop_var)) && length(prop_var) >= n_fac) {
      # Names map to the reordered list
      names(prop_var) <- original_factors 
    }
  } else {
    ss_loadings <- tapply(df_all$Loading^2, df_all$Factor, sum)
    prop_var <- as.numeric(ss_loadings / n_var)
    names(prop_var) <- names(ss_loadings)
  }
  
  if (max(prop_var, na.rm = TRUE) > 1) {
    prop_var <- prop_var / 100
  }
  
  # 3. Filter by threshold and reshape
  edges <- df_all |>
    subset(abs(Loading) >= threshold) |>
    data_rename(
      pattern = c("Variable", "Factor", "Loading"),
      replacement = c("from", "to", "weight")
    )
  
  # 4. Build a Manual Layout
  # Variables map to coordinates decreasing from n_var -> 1 (Places first item at the top)
  y_var <- seq(n_var, 1)
  
  y_fac <- seq(
    from = n_var - 0.5, 
    to = 1.5, 
    length.out = n_fac
  )
  
  nodes <- data.frame(
    name = c(original_factors, variables),
    type = c(rep("Factor", n_fac), rep("Variable", n_var)),
    x = c(rep(1, n_fac), rep(0, n_var)),
    y = c(y_fac, y_var),
    variance = c(prop_var[original_factors], rep(NA, n_var)),
    label_text = c(
      sprintf("%s\n(%.1f%%)", display_factors, prop_var[original_factors] * 100), 
      variables
    ),
    node_color = c(fac_colors, var_colors) # Append our mapped colors
  )
  
  # 5. Build the tidygraph object
  graph <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
  
  # 6. Plot using ggraph
  ggraph(graph, layout = "manual", x = x, y = y) + 
    
    # -- EDGES --
    geom_edge_link(
      aes(
        edge_width = abs(weight),
        edge_alpha = abs(weight),
        color = weight,
        label = sub("^(-?)0\\.", "\\1.", sprintf("%.2f", weight))
      ),
      arrow = arrow(length = unit(4, 'mm'), type = "closed"),
      start_cap = circle(0, 'mm'),    
      end_cap = circle(arrow_end_gap, 'snpc'), 
      angle_calc = 'along',
      label_dodge = unit(2.5, 'mm'),  
      label_size = loading_text_size
    ) +
    
    # -- FACTOR NODES --
    geom_node_point(
      aes(filter = type == "Factor", size = variance, fill = node_color),
      shape = 21,
      color = "white",
      stroke = 1.5,
      show.legend = FALSE
    ) +
    
    # -- FACTOR TEXT --
    geom_node_text(
      aes(filter = type == "Factor", label = label_text),
      color = "white",
      fontface = "bold",
      size = 3.5,
      lineheight = 0.9 
    ) +
    
    # -- VARIABLE NODES --
    geom_node_label(
      aes(filter = type == "Variable", label = label_text, fill = node_color),
      color = "white",
      fontface = "bold",
      size = 3.5,
      hjust = 1, 
      label.padding = unit(0.5, "lines"),
      show.legend = FALSE
    ) +
    
    # -- SCALES & AESTHETICS --
    scale_fill_identity() + # Evaluates our hex colors natively
    scale_size_continuous(range = factor_node_size, guide = "none") +
    scale_edge_color_gradient2(
      low = "#E74C3C", mid = "grey85", high = "#2ECC71",
      midpoint = 0, guide = "none" 
    ) +
    scale_edge_width_continuous(range = c(0.5, 2.5), guide = "none") +
    scale_edge_alpha_continuous(range = c(0.4, 1), guide = "none") +
    
    # -- CANVAS EXPANSION & THEME --
    scale_x_continuous(expand = expansion(add = expand)) +
    coord_cartesian(clip = "off") + 
    
    theme_graph() +
    theme(
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(20, 20, 20, 20) 
    ) +
    labs(title = "Factor Analysis Loadings")
}
```


## Descriptive

### Demographics

#### Age and Gender 

```{r}
gender_colors <- c("Female" = "#E91E63", "Male" = "#1976D2", "Other" = "#4CAF50")

df_age <- df |> filter(!is.na(Dem_Age), !is.na(Dem_Gender))
age_breaks <- seq(min(df_age$Dem_Age), max(df_age$Dem_Age), length.out = 51)
box_widths <- df_age |>
  group_by(Dem_Gender) |>
  summarise(max_count = max(hist(Dem_Age, breaks = age_breaks, plot = FALSE)$counts),
            .groups = "drop") |>
  mutate(box_width = max_count * 0.15)

p_age <- df_age |>
  left_join(box_widths, by = "Dem_Gender") |>
  ggplot(aes(y = after_stat(count), x = Dem_Age, fill = Dem_Gender, color = Dem_Gender)) +
  geom_histogram(aes(y = after_stat(count)), bins = 50, alpha = 0.4, color = NA) +
  geom_density(linewidth = 0.9, alpha = 0) +
  geom_boxplot(aes(y = 0, width = box_width), alpha = 0.5, outlier.size = 0, position = "identity") +
  facet_wrap(~Dem_Gender, ncol = 1, scales = "free_y") +
  scale_fill_manual(values = gender_colors, guide = "none") +
  scale_color_manual(values = gender_colors, guide = "none") +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold", size = 11, hjust = 1),
        panel.grid.minor = element_blank()) +
  labs(title = "Age Distribution", x = "Age", y = "Count")
p_age
```

#### Children

```{r}
# Number of children
p_children <- df |>
  filter(!is.na(Dem_Child_numb), Dem_Child_numb != "") |>
  count(Dem_Child_numb) |>
  mutate(Dem_Child_numb = factor(Dem_Child_numb,
    levels = c("I have no children", "1", "2", "3", "More than 3"))) |>
  ggplot(aes(x = Dem_Child_numb, y = n, fill = Dem_Child_numb)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Greens") +
  theme_minimal() +
  labs(title = "Number of Children", x = "", y = "Count")

# Parental leave
leave_levels <- c("Less than 2 weeks", "Between 2 weeks and 1 month",
                  "Between 1 month and 3 months", "Between 3 months and 6 months",
                  "Between 6 months and 1 year", "Between 1 year and 2 years",
                  "More than 2 years", "I did not take any parental leave")
p_parental <- df |>
  filter(!is.na(Dem_Parental_leave), Dem_Parental_leave != "") |>
  count(Dem_Parental_leave) |>
  mutate(Dem_Parental_leave = factor(Dem_Parental_leave, levels = leave_levels)) |>
  ggplot(aes(x = Dem_Parental_leave, y = n, fill = Dem_Parental_leave)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Blues") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Parental Leave", x = "", y = "Count")

p_children + p_parental
```

#### Research Discipline

```{r}
# Research discipline — pie chart
p_discipline <- df |>
  filter(!is.na(Work_Discipline), Work_Discipline != "") |>
  count(Work_Discipline) |>
  mutate(pct = n / sum(n),
         label = str_replace(Work_Discipline, " & ", "\n&"),
         label = paste0(label, "\n\n", n, " (", round(pct * 100), "%)")) |>
  ggplot(aes(x = "", y = n, fill = Work_Discipline)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") +
  geom_text(aes(label = label), position = position_stack(vjust = 0.5),
            size = 2.5, color = "white", fontface = "bold") +
  scale_fill_brewer(palette = "Set2") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Research Discipline")

# Highest diploma
p_diploma <- df |>
  filter(!is.na(Work_Diploma), Work_Diploma != "") |>
  count(Work_Diploma) |>
  mutate(Work_Diploma = factor(Work_Diploma,
    levels = c("Bachelor", "Master", "PhD", "Other"))) |>
  ggplot(aes(x = Work_Diploma, y = n, fill = Work_Diploma)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_brewer(palette = "Purples") +
  theme_minimal() +
  labs(title = "Highest Diploma", x = "", y = "Count")

p_discipline + p_diploma
```

#### Affiliation

```{r}
# Academic position
p_position <- df |>
  filter(!is.na(Work_Position), Work_Position != "") |>
  count(Work_Position) |>
  mutate(pct = n / sum(n) * 100) |>
  ggplot(aes(x = reorder(Work_Position, pct), y = n, fill = pct)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.1f%%", pct)), hjust = -0.15, size = 3, color = "grey30") +
  scale_y_continuous(expand = expansion(add = c(0, 50))) +
  scale_fill_gradient(low = "#b3cde3", high = "#084594") +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  labs(title = "Academic Position", x = "", y = "Count")

# Country of work + specific affiliations (dodged)
clean_country <- function(x) {
  x <- str_to_title(str_trim(x))
  case_when(
    x %in% c("Uk", "United Kingdom", "England", "Wales (Uk)", "Uk - England") ~ "United Kingdom",
    x %in% c("Be", "Belgique", "Belgium") ~ "Belgium",
    x %in% c("Nl", "The Netherlands") ~ "Netherlands",
    x %in% c("Usa", "United States") ~ "United States",
    x %in% c("Italia") ~ "Italy",
    x %in% c("Suisse") ~ "Switzerland",
    x %in% c("Feance", "Frabce", "France ", "France/Canada",
             "Germany And France", "Dijon", "Grenoble") ~ "France",
    .default = x
  )
}

normalize_affil <- function(x) {
  x <- str_trim(x)
  case_when(
    x == "" | is.na(x)                                                              ~ "Missing",
    str_detect(x, regex("^cnrs", ignore_case = TRUE))                               ~ "CNRS",
    str_detect(x, regex("^inserm", ignore_case = TRUE))                             ~ "INSERM",
    str_detect(x, regex("^inrae", ignore_case = TRUE))                              ~ "INRAE",
    str_detect(x, regex("^cea$", ignore_case = TRUE))                               ~ "CEA",
    str_detect(x, regex("^ens$", ignore_case = TRUE))                               ~ "ENS",
    str_detect(x, regex("^ucl$", ignore_case = TRUE))                               ~ "UCL",
    str_detect(x, regex("sorbonne univ|^sorbonne universit", ignore_case = TRUE))   ~ "Sorbonne Univ.",
    str_detect(x, regex("paris cit|upcit", ignore_case = TRUE))                     ~ "Univ. Paris Cité",
    str_detect(x, regex("sussex", ignore_case = TRUE))                              ~ "Univ. of Sussex",
    str_detect(x, regex("^ghent|universiteit gent", ignore_case = TRUE))            ~ "Ghent University",
    str_detect(x, regex("eth zurich|eth zürich|^eth$", ignore_case = TRUE))         ~ "ETH Zurich",
    str_detect(x, regex("^psl$|psl research|psl univ", ignore_case = TRUE))         ~ "PSL",
    str_detect(x, regex("toulouse", ignore_case = TRUE))                            ~ "Univ. de Toulouse",
    str_detect(x, regex("lille", ignore_case = TRUE))                               ~ "Univ. de Lille",
    str_detect(x, regex("grenoble", ignore_case = TRUE))                            ~ "Univ. Grenoble Alpes",
    str_detect(x, regex("bordeaux", ignore_case = TRUE))                            ~ "Univ. de Bordeaux",
    str_detect(x, regex("lyon", ignore_case = TRUE))                                ~ "Univ. de Lyon",
    str_detect(x, regex("strasbourg", ignore_case = TRUE))                          ~ "Univ. de Strasbourg",
    str_detect(x, regex("aix.marseille|aix marseille", ignore_case = TRUE))         ~ "Aix-Marseille Univ.",
    str_detect(x, regex("^bcbl$|basque center on cognition", ignore_case = TRUE))   ~ "BCBL",
    str_detect(x, regex("clermont", ignore_case = TRUE))                            ~ "Univ. Clermont",
    str_detect(x, regex("montpellier", ignore_case = TRUE))                         ~ "Univ. de Montpellier",
    str_detect(x, regex("paris.saclay|paris saclay", ignore_case = TRUE))           ~ "Univ. Paris-Saclay",
    str_detect(x, regex("paris 8", ignore_case = TRUE))                             ~ "Univ. Paris 8",
    str_detect(x, regex("^ulb$|ulb,|libre de bruxelles", ignore_case = TRUE))       ~ "ULB",
    str_detect(x, regex("leiden", ignore_case = TRUE))                              ~ "Leiden University",
    str_detect(x, regex("picardie", ignore_case = TRUE))                            ~ "Univ. Picardie",
    str_detect(x, regex("côte d.azur|cote d.azur", ignore_case = TRUE))             ~ "Univ. Côte d'Azur",
    str_detect(x, regex("rennes", ignore_case = TRUE))                              ~ "Univ. de Rennes",
    str_detect(x, regex("groningen", ignore_case = TRUE))                           ~ "Univ. of Groningen",
    str_detect(x, regex("caen", ignore_case = TRUE))                                ~ "Univ. de Caen",
    str_detect(x, regex("minho", ignore_case = TRUE))                               ~ "Univ. of Minho",
    str_detect(x, regex("turin", ignore_case = TRUE))                               ~ "Univ. of Turin",
    .default = x
  )
}

# Include ALL rows; normalize_affil returns "Missing" for empty/NA
df_country_aff_all <- df |>
  filter(!is.na(Work_Country), Work_Country != "") |>
  mutate(
    Country = clean_country(Work_Country),
    Affiliation = normalize_affil(Work_Affiliation)
  )

country_palette_ext <- c(
  "France"         = "#1976D2",
  "United Kingdom" = "#E91E63",
  "Germany"        = "#FF9800",
  "Spain"          = "#8BC34A",
  "Belgium"        = "#9C27B0",
  "Italy"          = "#00BCD4",
  "Netherlands"    = "#F44336",
  "Switzerland"    = "#795548",
  "United States"  = "#607D8B",
  "Other country"  = "#C8E6C9",
  "—"              = "#BDBDBD"   # for Missing / Other affiliation buckets
)

# Named affiliations = those with n >= 3 after normalisation
named_affils <- df_country_aff_all |>
  filter(Affiliation != "Missing") |>
  count(Affiliation, sort = TRUE) |>
  filter(n >= 2) |>
  pull(Affiliation)

df_plot_affil <- df_country_aff_all |>
  mutate(
    Affiliation_cat = case_when(
      Affiliation == "Missing"          ~ "Missing",
      Affiliation %in% named_affils     ~ Affiliation,
      .default                          = "Other"
    ),
    Country_fill = case_when(
      Affiliation_cat %in% c("Missing", "Other") ~ "—",
      Country %in% names(country_palette_ext)     ~ Country,
      .default                                     = "Other country"
    )
  ) |>
  count(Affiliation_cat, Country_fill)

# Order: by total count, with Other/Missing pinned at the bottom
affil_totals <- df_plot_affil |>
  group_by(Affiliation_cat) |>
  summarise(total = sum(n), .groups = "drop") |>
  mutate(rank = case_when(
    Affiliation_cat == "Missing" ~ -2L,
    Affiliation_cat == "Other"   ~ -1L,
    .default = as.integer(total)
  )) |>
  arrange(rank)

affil_level_order <- affil_totals$Affiliation_cat

affil_label_df <- affil_totals |>
  mutate(Affiliation_cat = factor(Affiliation_cat, levels = rev(affil_level_order)))

p_country <- df_plot_affil |>
  mutate(Affiliation_cat = factor(Affiliation_cat, levels = affil_level_order)) |>
  ggplot(aes(x = Affiliation_cat, y = n, fill = Country_fill)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(data = affil_label_df,
            aes(x = Affiliation_cat, y = total, label = total),
            inherit.aes = FALSE,
            hjust = -0.2, size = 3, color = "grey30") +
  scale_fill_manual(values = country_palette_ext, name = "Country") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "right",
        legend.text = element_text(size = 7.5),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y = element_text(size = 8)) +
  labs(title = "Affiliations",
       x = "", y = "Count")

p_position + p_country
```

```{r}
# Time allocation across research activities
p_activities <- df |>
  select(Work_Time_Research, Work_Time_Teaching, Work_Time_Administration,
         Work_Time_Popularization, Work_Time_Other) |>
  rename(Research = Work_Time_Research,
         Teaching = Work_Time_Teaching,
         Administration = Work_Time_Administration,
         Popularization = Work_Time_Popularization,
         Other = Work_Time_Other) |>
  pivot_longer(everything(), names_to = "Activity", values_to = "Percentage") |>
  filter(!is.na(Percentage)) |>
  mutate(Activity = factor(Activity,
    levels = c("Research", "Teaching", "Administration", "Popularization", "Other")),
    Percentage = Percentage / 100) |>
  ggplot(aes(x = Activity, y = Percentage, fill = Activity)) +
  geom_violin(alpha = 0.6, trim = TRUE) +
  geom_boxplot(width = 0.1, fill = "white", outlier.size = 0.5) +
  scale_fill_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Time Allocation Across Activities", x = "", y = "Proportion of Work Time")
p_activities
```

#### Careers 

```{r}
# Career perceptions: scatterplot matrix with ggside marginals
pub_colors <- c("Yes" = "#1976D2", "No" = "#E91E63")

df_career <- df |>
  filter(!is.na(Work_Publication)) |>
  transmute(
    Published = Work_Publication,
    Prob_Perm = Work_Probability_permanent_position / 100,
    Sat_Numb  = Work_Satisfaction_numb_publications  / 100,
    Sat_Qual  = Work_Satisfaction_quality_publications / 100
  )

make_scatter_side <- function(data, xv, yv, xl, yl) {
  ggplot(data |> filter(!is.na(.data[[xv]]), !is.na(.data[[yv]])),
         aes(x = .data[[xv]], y = .data[[yv]])) +
    geom_point(alpha = 0.3, size = 2, color = "#1976D2") +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.12, linewidth = 0.8,
                color = "#1976D2", fill = "#1976D2") +
    geom_xsidehistogram(bins = 15, alpha = 0.5, fill = "#1976D2") +
    geom_ysidehistogram(bins = 15, alpha = 0.5, fill = "#1976D2") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_bw() +
    theme(ggside.panel.scale = 0.25,
          ggside.panel.border = element_blank(),
          ggside.panel.background = element_blank(),
          ggside.axis.ticks.x = element_blank(),
          ggside.axis.ticks.y = element_blank()) +
    labs(x = xl, y = yl)
}

p_ab <- make_scatter_side(df_career, "Prob_Perm", "Sat_Numb",
                          "P(Permanent Position)", "Sat. No. Publications")
p_ac <- make_scatter_side(df_career, "Prob_Perm", "Sat_Qual",
                          "P(Permanent Position)", "Sat. Quality Publications")
p_bc <- make_scatter_side(df_career, "Sat_Numb", "Sat_Qual",
                          "Sat. No. Publications", "Sat. Quality Publications")

p_pub_bar <- df |>
  filter(!is.na(Work_Publication), Work_Publication != "") |>
  count(Work_Publication) |>
  ggplot(aes(x = Work_Publication, y = n, fill = Work_Publication)) +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
  scale_fill_manual(values = pub_colors) +
  theme_bw() +
  labs(title = "Has Published?", x = "", y = "Count")

(p_ab | p_ac) / (p_bc | p_pub_bar) +
  plot_annotation(
    title = "Career Perceptions — Pairwise Relationships",
    theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5))
  )
```

```{r}
# Committee/service involvement and clinical activity
p_commit <- df |>
  filter(!is.na(Work_Committees), Work_Committees != "") |>
  count(Work_Committees) |>
  ggplot(aes(x = Work_Committees, y = n, fill = Work_Committees)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("Yes" = "#4dac26", "No" = "#d01c8b")) +
  theme_minimal() +
  labs(title = "Member of Committees", x = "", y = "Count")

p_clinical <- df |>
  filter(!is.na(Work_Clinical_activity), Work_Clinical_activity != "") |>
  count(Work_Clinical_activity) |>
  ggplot(aes(x = Work_Clinical_activity, y = n, fill = Work_Clinical_activity)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("Yes" = "#4dac26", "No" = "#d01c8b")) +
  theme_minimal() +
  labs(title = "Clinical Activity", x = "", y = "Count")


(p_commit + p_clinical) 
```

### Science Quality Criteria

#### Overview

```{r}
# Quality criteria importance (binary endorsement rates)
df_quality <- df |>
  select(starts_with("Work_Criteria_quality_science_")) |>
  rename_with(~str_remove(., "Work_Criteria_quality_science_")) |>
  rename_with(~recode(.,
    "Originality"               = "Originality / Innovation",
    "Significance"              = "Significance / Impact",
    "Rigorous_meth"             = "Rigorous Methodology",
    "Relevance-data-analyses"   = "Appropriate Statistics",
    "high-IF"                   = "High Impact Factor Journal",
    "Transparence"              = "Transparency / Open Science",
    "Replication"               = "Replication",
    "Environmental-impact"      = "Environmental Impact",
    "Inclusivity"               = "Inclusivity / Diversity"
  ))

p_criteria <- df_quality |>
  pivot_longer(everything(), names_to = "Criterion", values_to = "Endorsed") |>
  filter(!is.na(Endorsed)) |>
  group_by(Criterion) |>
  summarise(pct = mean(Endorsed == "Yes"), .groups = "drop") |>
  ggplot(aes(x = reorder(Criterion, pct), y = pct, fill = pct)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(low = "#fee8c8", high = "#b30000", guide = "none") +
  scale_y_continuous(labels = scales::percent_format()) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Endorsement of Quality Criteria for Science",
       x = "", y = "% endorsing")

p_criteria
```

```{r}
df_quality_num <- df_quality |>
  mutate(across(everything(), ~as.numeric(. == "Yes")))

p_criteria_cor <- correlation(df_quality_num, method = "pearson", redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x = Parameter1, y = Parameter2, fill = r)) +
  geom_tile() +
  geom_text(aes(label = label), color = "black", size = 3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3", "white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Co-endorsement of Science Quality Criteria",
       x = "", y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_criteria_cor

rez_criteria <- n_components(df_quality_num)
plot(rez_criteria)

pca_criteria <- principal_components(df_quality_num, n = 8)
plot(pca_criteria)

# Extract loadings
as.data.frame(pca_criteria) |> 
  select(Variable, PC1, PC2) |> 
  data_rename(c("Novel and Impactful vs. Rigourous and Transparent" = "PC1", 
                "Rigorous and Innovative vs. Virtuous" = "PC2")) |> 
  pivot_longer(-Variable, names_to = "Component", values_to = "Loading") 
 # TODO: Make loading plot
  

```

#### Predictors

```{r}
df_quality2 <- predict(pca_criteria, names = c("Criteria1", "Criteria2")) |> 
  cbind(df)


m_criteria1 <- brms::brm(Criteria1 ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df_quality2 |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male"), Dem_Age <= 70),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")
m_criteria2 <- brms::brm(Criteria2 ~ Dem_Gender * poly(Dem_Age, 2), 
                     data = df_quality2 |> 
                       mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |> 
                       filter(Dem_Gender %in% c("Female", "Male"), Dem_Age <= 70),
                     backend = "cmdstanr",
                     algorithm = "pathfinder")


p_criteria_pred1 <- rbind(
  mutate(estimate_relation(m_criteria1, length = 40), Outcome = "Novel and Impactful vs. Rigourous and Transparent"),
  mutate(estimate_relation(m_criteria2, length = 40), Outcome = "Rigorous and Innovative vs. Virtuous")
) |>
  ggplot(aes(x = Dem_Age, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Outcome, 
                  group = interaction(Dem_Gender, Outcome)), alpha = 0.1) +
  geom_line(aes(color=Outcome, linetype = Dem_Gender), linewidth = 1) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  scale_colour_discrete(palette="Set1") +
  scale_fill_discrete(palette="Set1") +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Score", x = "Age",
       fill = "Outcome", color = "Outcome", linetype = "Gender",
       title = "Research Quality Criteria") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5))
p_criteria_pred1
```


### Open Science

#### Overview

```{r}
df_os_practices <- select(df, starts_with("OS_"), -starts_with("OS_Help")) |>
  rename(
    "OS Familiarity" = OS_Familiar,
    "OS Importance" = OS_Importance,
    "OS Training" = OS_Workshops,
    "View on Preregistration" = OS_Study_Preregistration,
    "View on Registered Reports" = OS_Registered_Reports,
    "View on Open Materials" = OS_Open_Materials,
    "View on Open Data" = OS_Open_Data,
    "View on Open Peer Review" = OS_Open_Peer_Review,
    "View on Open Access" = OS_Open_Access_Publication,
    "View on Replication Studies" = OS_Replication_Studies,
    "View on Participatory Research" = OS_Participatory_Research
  )

p_os_prac1 <- correlation(df_os_practices, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Co-occurrence of Open Science Practice Engagement",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5))
p_os_prac1

rez <- n_factors(df_os_practices)
plot(rez)

f <- factor_analysis(df_os_practices, n=3)
plot(f)
p_os_prac2 <- plot_graph(f, threshold = 0.2, arrow_end_gap = 0.12, expand = c(1.5, 0.5))
p_os_prac2
```

#### Open Science Help


```{r}
df_os_help <- select(df, starts_with("OS_Help"), -OS_Help_Other)
names(df_os_help) <- str_replace(names(df_os_help), "OS_Help_", "") |>
  str_replace_all(fixed("_"), " ") |>
  recode(
    "Ethical issues"                  = "Data sharing\nethics",
    "Workload"                         = "Dedicated OS\nworkload",
    "Infrastructure"                   = "Technical\ninfrastructure",
    "Funding"                          = "Dedicated\nfunding",
    "Incentives Fund Institutions"     = "Institutional\nincentives",
    "Recognition Promotion Recruitment" = "Career\nrecognition",
    "Support Seniors"                  = "Senior researcher\nsupport",
    "Support Juniors"                  = "Junior researcher\nsupport",
    "Training"                         = "OS training"
  )

correlation(df_os_help, redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Open Science Help Avenues",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


p_os_help <- df_os_help |>
  mutate(participant = paste0("S", 1:nrow(df_os_help))) |>
  pivot_longer(-participant) |>
  summarize(Total = sum(value) / nrow(df_os_help), .by="name") |>
  mutate(Type = case_when(
           name %in% c("Career\nrecognition") ~ "Recognition",
           name %in% c("Institutional\nincentives", "Dedicated\nfunding") ~ "Money",
           name %in% c("Time", "Dedicated OS\nworkload") ~ "Time",
           name %in% c("Technical\ninfrastructure", "Senior researcher\nsupport", "OS training", "Junior researcher\nsupport") ~ "Support",
           .default = "Other"),
         Type = fct_relevel(Type, "Recognition", "Money", "Time", "Support"),
         name = fct_reorder(name, desc(Total))) |>
  ggplot(aes(x = name, y = Total, fill = Type)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Recognition" = "#E91E63", "Money" = "gold", "Time" = "#4CAF50", "Support" = "#1E88E5", "Other" = "grey")) +
  theme_minimal() +
  labs(title = "What would you need to further adopt open science practices?",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 50, hjust = 1),
        plot.title = element_text(size = 12, face = "bold", hjust = 0))
p_os_help
```


### Slow Science

```{r}
df_ss_scales <- select(df, SS_Familiar, SS_Importance, SS_Workshops)

df_ss_scales |>
  rename(
    "SS Familiarity" = SS_Familiar,
    "SS Importance" = SS_Importance,
    "SS Training\n(Workshops)" = SS_Workshops
  ) |>
  correlation(redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=3) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Slow Science Scales",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Slow Science Definition

```{r}
df_ss_def <- select(df, starts_with("SS_Definition_"), -SS_Definition_Other)
names(df_ss_def) <- str_replace(names(df_ss_def), "SS_Definition_", "") |>
  str_replace_all(fixed("_"), " ")

ss_def <- df_ss_def |>
  mutate(participant = paste0("S", 1:nrow(df_ss_def))) |>
  pivot_longer(-participant) |>
  mutate(name = recode(name,
    "Quality over quantity"    = "Quality over\nquantity",
    "Slow Process"             = "Slow process over\nshort-term goals",
    "Work Life Balance"        = "Better work/life\nbalance",
    "Changing Metrics"         = "Changing assessment\nmetrics",
    "Increase Research Time"   = "Increase time\nfor research",
    "Diminishing Publications" = "Fewer\npublications"
  )) |>
  summarize(Total = sum(value, na.rm = TRUE) / nrow(df_ss_def), .by = "name") |>
  mutate(name = fct_reorder(name, desc(Total))) |>
  ggplot(aes(x = name, y = Total, fill=Total)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_gradient(low = "lightblue", high = "steelblue", guide = "none") +
  theme_minimal() +
  labs(title = "Which of these best describes Slow Science for you?",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1),
        plot.title = element_text(size = 12, face = "bold", hjust = 0))
ss_def
```

### Slow Science Feasibility

```{r}
ss_feas <- select(df, matches("^SS_.*Feasible_individual$|^SS_.*Feasible_institution$|^SS_.*Not_Feasible$")) |>
  mutate(participant = paste0("S", seq_len(n()))) |>
  pivot_longer(-participant, names_to = "Variable", values_to = "value") |>
  mutate(
    Practice = case_when(
      str_detect(Variable, "_Limit_publication_") ~ "Limit nr. of articles\nsubmitted for publication",
      str_detect(Variable, "_Replicate_")         ~ "Replicate before\npublishing",
      str_detect(Variable, "_Longertime_")        ~ "Think in longer\ntimescales",
      str_detect(Variable, "_Models_")            ~ "Provide models for\nthe next generation",
      str_detect(Variable, "_Quality_")           ~ "Assess quality,\nnot quantity",
      str_detect(Variable, "_Teamwork_")          ~ "Value teamwork over\nindividual work",
      str_detect(Variable, "_Onepublication_")    ~ "Publish only 1\narticle per year",
      str_detect(Variable, "_Onegrant_")          ~ "Only 1 grant\nper year"
    ),
    Level = case_when(
      str_detect(Variable, "_Feasible_individual$") ~ "Individual",
      str_detect(Variable, "_Feasible_institution$") ~ "Institution",
      str_detect(Variable, "_Not_Feasible$") ~ "Not Feasible"
    ),
    Level = fct_relevel(Level, "Individual", "Institution", "Not Feasible")
  ) |>
  summarize(Proportion = sum(value, na.rm = TRUE) / n_distinct(participant),
            .by = c(Practice, Level)) |> 
  mutate(Practice = fct_reorder(Practice, ifelse(Level == "Institution", Proportion, 0), .fun = \(x) sum(x, na.rm = TRUE), .desc = TRUE)) |>
  ggplot(aes(x = Practice, y = Proportion, fill = Level)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Individual" = "#4CAF50", "Institution" = "#1E88E5", "Not Feasible" = "#E53935")) +
  theme_minimal() +
  labs(title = "Who Can Help Slow Science?",
       x = "", y = "", fill = NULL) +
  theme(axis.text.x = element_text(angle = 40, hjust = 1),
        plot.title = element_text(size = 12, face = "bold", hjust = 0))
ss_feas
```



## Structure of Science Practices

Alternative names:
- Agathic Science
- Honest Science
- New Science

### Correlation

```{r}
df_resprac <- select(df, starts_with("OS_"), starts_with("GS_"), -starts_with("OS_Help"),
                     -OS_Workshops,
                     -OS_Familiar,
                     SS_Importance, SS_Familiar,
                     ES_Importance_research_team, ES_Consequences_society) |> 
  rename("Open Science - Importance" = OS_Importance,
         # "Open Science - Familiarity" = OS_Familiar,
         "Slow Science - Importance" = SS_Importance,
         "Slow Science - Familiarity" = SS_Familiar,
         # How important do you consider the diversity of the research team (in terms 
         # of neurodiversity, disability, ethnicity, gender, etc.)?
         "Ethical Science - Team Diversity" = ES_Importance_research_team,
         # How important is it to be careful regarding the direct consequences (e.g.
         # benefits or harms) for the participants or society of your research?
         "Ethical Science - Societal Consequences" = ES_Consequences_society,
         # Green Science
         # How important is environmental sustainability in how you conduct your research?
         "Green Science - Ecofriendly Practices" = GS_Importance_conducting,
         # How important is environmental sustainability in choosing research topics?
         "Green Science - Ecofriendly Topics" = GS_Importance_topic,
         # Have you changed your research practices (e.g., experimental design, topic, material)
         # for environmental sustainability reasons?
         "Green Science - Changed Practices" = GS_Changes_practices,
         # Have you changed your research communication practices (e.g., professional travels)
         # for environmental sustainability reasons?
         "Green Science - Changed Communication" = GS_Changes_communication_practices,
         # Do you think there is a link between scientific production and environmental sustainability? 
         "Green Science - Belief Relation" = GS_Relation_Research_Sustainability,
         # Would you agree to change your research practices for environmental reasons?
         "Green Science - Change Willingness" = GS_Change_practices_agreeing,
         "Endorsement - Participatory Research" = OS_Participatory_Research,
         "Endorsement - Replication Studies" = OS_Replication_Studies,
         "Endorsement - Open Access" = OS_Open_Access_Publication,
         "Endorsement - Open Peer Review" = OS_Open_Peer_Review,
         "Endorsement - Open Data" = OS_Open_Data,
         "Endorsement - Open Materials" = OS_Open_Materials,
         "Endorsement - Registered Reports" = OS_Registered_Reports,
         "Endorsement - Preregistration" = OS_Study_Preregistration)


p_cor <- df_resprac |>
  correlation(redundant = TRUE) |>
  correlation::cor_sort() |>
  as.data.frame() |>
  mutate(label = ifelse(p < .001, format_value(r, digits = 2), "")) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), color="black", size=1.5) +
  annotate(geom="rect", xmin=0.5, xmax=8.5, ymin=0.5, ymax=8.5, alpha=0, color="#9C27B0", linewidth = 2) +
  annotate(geom="rect", xmin=0.55, xmax=4.5, ymin=0.55, ymax=4.5, alpha=0, color="#4CAF50", linewidth = 2) +
  annotate(geom="rect", xmin=8.5, xmax=11.5, ymin=8.5, ymax=11.5, alpha=0, color="#3F51B5", linewidth = 2) +
  annotate(geom="rect", xmin=17.5, xmax=19.5, ymin=17.5, ymax=19.5, alpha=0, color="#FF9800", linewidth = 2) +
  annotate(geom="rect", xmin=13.5, xmax=17.5, ymin=13.5, ymax=17.5, alpha=0, color="#2196F3", linewidth = 2) +
  scale_fill_gradientn(colours = c("darkblue", "blue", "#2196F3","white", "#FFC107", "#F44336", "darkred"), limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Correlation Matrix of Research Values",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 35, hjust = 1),
        plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
        legend.position = "none")
p_cor
```


### EFA

```{r}
rez_resprac <- n_factors(df_resprac)
plot(rez_resprac)

f <- factor_analysis(df_resprac, n=5, rotation = "oblimin")
plot(f)

color_vars_resprac <- c(
  # GS variables (green)
  "Green Science - Ecofriendly Practices"                  = "#4CAF50",
  "Green Science - Ecofriendly Practices" = "#4CAF50",
  "Green Science - Ecofriendly Topics" = "#4CAF50",
  "Green Science - Changed Practices" = "#4CAF50",
  "Green Science - Changed Communication" = "#4CAF50",
  "Green Science - Belief Relation" = "#4CAF50",
  "Green Science - Change Willingness" =  "#4CAF50",
  # OS variables (blue)
  "Endorsement - Open Data"                 = "#2196F3",
  "Endorsement - Open Materials"            = "#2196F3",
  "Endorsement - Open Access"               = "#2196F3",
  "Open Science - Importance"               = "#2196F3",
  "Endorsement - Open Peer Review"          = "#2196F3",
  
  "Endorsement - Preregistration"           = "#3F51B5",
  "Endorsement - Registered Reports"        = "#3F51B5",
  "Endorsement - Replication Studies"       = "#3F51B5",
  "Endorsement - Participatory Research"    = "#3F51B5",
  
  # SS variable (teal)
  "Slow Science - Importance"               = "#FF9800",
  "Slow Science - Familiarity"              = "#FF9800",
  
  # ES variables (purple)
  "Ethical Science - Team Diversity"        = "#9C27B0",
  "Ethical Science - Societal Consequences" = "#9C27B0"
)

p_resprac <- plot_graph(f, threshold = 0.2, arrow_end_gap = 0.12, expand = c(1, 0.5),
                        names_factors = list("Green Science" = "MR1", "Rigorous\nScience" = "MR2", "Ethical\nScience" = "MR5", 
                                             "Slow Science" = "MR3", "Open\nScience" = "MR4"),
                        color_factors = c("MR1" = "#4CAF50", "MR4" = "#2196F3", "MR2" = "#3F51B5",
                                          "MR3" = "#FF9800", "MR5" = "#9C27B0"),
                        color_variables = color_vars_resprac)
p_resprac
```

### CFA

```{r}
# Raw-name to display-name mapping (matches df_resprac rename calls)
cfa_labels <- c(
  "Open_Science"                  = "Open\nScience",
  "Rigorous_Science"              = "Rigorous\nScience",
  "Green_Science"                 = "Green\nScience",
  "Slow_Science"                  = "Slow\nScience",
  "Ethical_Science"               = "Ethical\nScience",
  "OS_Importance"                 = "OS\nImportance",
  "OS_Open_Data"                  = "Open\nData",
  "OS_Open_Materials"             = "Open\nMaterials",
  "OS_Open_Access_Publication"    = "Open\nAccess",
  "OS_Open_Peer_Review"           = "Open\nPeer Review",
  "OS_Study_Preregistration"      = "Prereg.",
  "OS_Registered_Reports"         = "Reg.\nReports",
  "OS_Replication_Studies"        = "Replication\nStudies",
  "OS_Participatory_Research"     = "Participatory\nResearch",
  "GS_Importance_conducting"       = "Importance\n(Conducting)",
  "GS_Importance_topic"            = "Importance\n(Topic)",
  "GS_Changes_practices"           = "Changed\nPractices",
  "GS_Changes_communication_practices" = "Changed\nCommunication",
  "GS_Relation_Research_Sustainability" = "Belief\nin Link",
  "GS_Change_practices_agreeing"  = "Change\nWillingness",
  "SS_Importance"                 = "SS\nImportance",
  "SS_Familiar"                   = "SS\nFamiliarity",
  "ES_Importance_research_team"   = "Team\nDiversity",
  "ES_Consequences_society"       = "Societal\nConseq."
)

cfa_node_colors <- c(
  "Open_Science"               = "#2196F3",
  "Rigorous_Science"           = "#3F51B5",
  "Green_Science"              = "#4CAF50",
  "Slow_Science"               = "#FF9800",
  "Ethical_Science"            = "#9C27B0",
  "OS_Importance"              = "#2196F3",
  "OS_Open_Data"               = "#2196F3",
  "OS_Open_Materials"          = "#2196F3",
  "OS_Open_Access_Publication" = "#2196F3",
  "OS_Open_Peer_Review"        = "#2196F3",
  "OS_Study_Preregistration"   = "#3F51B5",
  "OS_Registered_Reports"      = "#3F51B5",
  "OS_Replication_Studies"     = "#3F51B5",
  "OS_Participatory_Research"  = "#3F51B5",
  "GS_Importance_conducting"   = "#4CAF50",
  "GS_Importance_topic"        = "#4CAF50",
  "GS_Changes_practices"       = "#4CAF50",
  "GS_Changes_communication_practices" = "#4CAF50",
  "GS_Relation_Research_Sustainability" = "#4CAF50",
  "GS_Change_practices_agreeing" = "#4CAF50",
  "SS_Importance"              = "#FF9800",
  "SS_Familiar"                = "#FF9800",
  "ES_Importance_research_team"= "#9C27B0",
  "ES_Consequences_society"    = "#9C27B0"
)

# Manual CFA model using raw df column names
cfa_model <- "
  Open_Science     =~ OS_Importance +
                      OS_Open_Data +
                      OS_Open_Materials +
                      OS_Open_Access_Publication +
                      OS_Open_Peer_Review
  Rigorous_Science =~ OS_Study_Preregistration +
                      OS_Registered_Reports +
                      OS_Replication_Studies +
                      OS_Participatory_Research
  Green_Science    =~ GS_Importance_conducting +
                      GS_Importance_topic +
                      GS_Changes_practices +
                      GS_Changes_communication_practices +
                      GS_Relation_Research_Sustainability +
                      GS_Change_practices_agreeing
  Slow_Science     =~ SS_Importance +
                      SS_Familiar
  Ethical_Science  =~ ES_Importance_research_team +
                      ES_Consequences_society
"

library(lavaan)
library(tidySEM)

fit_cfa <- cfa(cfa_model, data = df, std.lv = TRUE)

model_parameters(fit_cfa, standardize = TRUE) 
model_performance(fit_cfa)

# ── Manual ggraph/tidygraph CFA plot ─────────────────────────────────────────

# 1. Node positions (manual x/y grid matching the layout intent)
cfa_pos <- tribble(
  ~name,                        ~x,   ~y,
  # Rigorous Science factor + vars (left, top half)
  "OS_Study_Preregistration",    0,   9,
  "OS_Registered_Reports",       1,   10,
  "OS_Replication_Studies",      2,   10,
  "OS_Participatory_Research",   3,   9,
  "Rigorous_Science",            1,   8,
  # Open Science factor + vars (left, bottom half)
  "Open_Science",                1,    2.5,
  "OS_Open_Materials",           0,    1,
  "OS_Open_Data",                1,    0,
  "OS_Open_Access_Publication",  2,    0,
  "OS_Importance",               3,    1,
  "OS_Open_Peer_Review",         4,    2,
  # Slow Science factor + vars (centre)
  "SS_Importance",               6,   10,
  "Slow_Science",                6,    5,
  "SS_Familiar",                 6,    0,
  # Green Science factor + vars (right, top half)
  "Green_Science",              11,    7.5,
  "GS_Importance_conducting",              12,   9,
  "GS_Importance_topic",                  11.5,   10,
  "GS_Change_practices_agreeing",         10.5,   10,
  "GS_Changes_practices",                 9.65,    9.75,
  "GS_Changes_communication_practices",   9,   9,
  "GS_Relation_Research_Sustainability",  8.75,   7.75,
  
  # Ethical Science factor + vars (right, bottom half)
  "Ethical_Science",            11,    2.5,
  "ES_Importance_research_team",10,    0,
  "ES_Consequences_society",    12,    0
)

# 2. Extract edges from lavaan (loadings + significant factor correlations)
cfa_params <- lavaan::parameterEstimates(fit_cfa, standardized = TRUE) |>
  filter(op %in% c("=~", "~~"),
         !(op == "~~" & lhs == rhs),          # drop self-variances
         !(op == "~~" & pvalue >= 0.05)) |>   # drop non-sig correlations
  mutate(est_std = ifelse(is.na(std.all), est, std.all))

# 3. Build tidygraph object
all_nodes <- cfa_pos |>
  mutate(
    fill       = cfa_node_colors[name],
    node_label = cfa_labels[name],
    shape      = ifelse(name %in% c("Open_Science","Rigorous_Science",
                                    "Green_Science","Slow_Science","Ethical_Science"),
                        "factor", "indicator")
  )

edge_df <- cfa_params |>
  transmute(
    from      = lhs,
    to        = rhs,
    op        = op,
    est_std   = est_std,
    edge_col  = ifelse(op == "~~", "#4CAF50", "grey50"),
    edge_lwd  = ifelse(op == "~~", abs(est_std) * 3, 0.6),
    edge_type = ifelse(op == "~~", "dashed", "solid"),
    edge_label = sub("^0\\.", ".", sub("^-0\\.", "-.", sprintf("%.2f", est_std)))
  )

g_tidy <- tbl_graph(nodes = all_nodes, edges = edge_df, directed = TRUE,
                    node_key = "name")

# 4. Plot
p_cfa <- ggraph(g_tidy, layout = "manual", x = x, y = y) +
  # Loading arrows (=~)
  geom_edge_link(
    aes(filter = op == "=~", label = edge_label, edge_colour = edge_col, edge_width = edge_lwd),
    arrow = arrow(length = unit(2.5, "mm"), type = "closed"),
    label_size = 2.5, label_colour = "grey30", angle_calc = "along", label_dodge = unit(2, "mm"),
    end_cap = circle(5, "mm"),
    show.legend = FALSE
  ) +
  # Factor-correlation arcs (~~)
  geom_edge_bend(
    aes(filter = op == "~~", edge_colour = edge_col, edge_width = edge_lwd, label = edge_label),
    strength = 0.3,
    # arrow = arrow(length = unit(2.5, "mm"), ends = "both", type = "open"),
    label_size = 2.5, label_colour = "grey30", angle_calc = "along", label_dodge = unit(2.5, "mm"),
    show.legend = FALSE
  ) +
  scale_edge_colour_identity() +
  scale_edge_width_continuous(range = c(0.6, 2.5)) +
  # Indicator nodes (rectangles → points with shape 22)
  geom_node_point(
    aes(filter = shape == "indicator", fill = fill),
    shape = 22, size = 12, colour = "white", show.legend = FALSE, stroke = NA
  ) +
  # Factor nodes (circles)
  geom_node_point(
    aes(filter = shape == "factor", fill = fill),
    shape = 21, size = 30, show.legend = FALSE, stroke = NA
  ) +
  scale_fill_identity() +
  geom_node_text(aes(filter = shape == "factor", label = node_label), size = 3, lineheight = 0.85, color = "white", fontface = "bold") +
  geom_node_text(aes(filter = shape == "indicator", label = node_label), size = 2.8, lineheight = 0.85) +
  labs(title = "Structural Model") +
  theme_void() +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5))

p_cfa
```



### Clustering

```{r}
df_resprac_fac <- as.data.frame(predict(fit_cfa))

n_clusters(df_resprac_fac) |>
  plot()

rez <- cluster_analysis(df_resprac_fac, n=5, method="hkmeans")
plot(rez)
rez

df_resprac_fac$Profile <- predict(rez)
df_resprac_fac <- mutate(df_resprac_fac, Profile = case_when(
           Profile == 1 ~ "Cluster 1\nIdealists",
           Profile == 2 ~ "Cluster 2\nEthical Productivists",
           Profile == 3 ~ "Cluster 3\nQuality Champions",
           Profile == 4 ~ "Cluster 4\nEthical Radicalists",
           .default = "Cluster 5\nTraditionalists"
         ))
```

```{r}
cluster_vars <- names(as.data.frame(predict(fit_cfa)))
labels <- tibble(Variable = cluster_vars, label = str_replace(cluster_vars, "_", "\n"))



n_vars  <- length(cluster_vars)
angles  <- seq(0, 2 * pi, length.out = n_vars + 1)[seq_len(n_vars)]

# Cluster means, normalised to [0,1] using full-data range per variable
var_mins <- sapply(cluster_vars, \(v) min(df_resprac_fac[[v]], na.rm = TRUE))
var_maxs <- sapply(cluster_vars, \(v) max(df_resprac_fac[[v]], na.rm = TRUE))

radar_means <- df_resprac_fac |>
  group_by(Profile) |>
  summarise(across(all_of(cluster_vars), \(x) mean(x, na.rm = TRUE)), .groups = "drop")

for (v in cluster_vars) {
  radar_means[[v]] <- (radar_means[[v]] - var_mins[v]) / (var_maxs[v] - var_mins[v])
}

# Long format with (x, y) cartesian coords
radar_long <- radar_means |>
  pivot_longer(-Profile, names_to = "Variable", values_to = "r") |>
  left_join(tibble(Variable = cluster_vars, angle = angles), by = "Variable") |>
  mutate(x = r * sin(angle), y = r * cos(angle))

# Close each polygon by appending the first point again
radar_closed <- radar_long |>
  group_by(Profile) |>
  group_modify(\(d, .y) bind_rows(d, d[1, ])) |>
  ungroup()

# Background grid (concentric circles + spokes)
grid_circles <- expand.grid(r = c(.25, .5, .75, 1), theta = seq(0, 2 * pi, length.out = 200)) |>
  mutate(x = r * sin(theta), y = r * cos(theta), r = factor(r))

spokes <- tibble(Variable = cluster_vars, angle = angles) |>
  mutate(x1 = sin(angle), y1 = cos(angle))

# Use left_join instead of named-vector indexing to avoid NA from tibble column lookup
axis_labels <- spokes |>
  left_join(labels, by = "Variable") |>
  mutate(lx = 1.25 * sin(angle), ly = 1.25 * cos(angle))

# Profile counts and percentages for annotation
profile_counts <- df_resprac_fac |>
  count(Profile) |>
  mutate(pct   = n / sum(n) * 100,
         label = paste0("N = ", n, " (", round(pct), "%)"))

all_profiles <- unique(radar_closed$Profile)

# Retrieve the Set1 colours for profile labelling
set1_cols <- RColorBrewer::brewer.pal(max(3, length(all_profiles)), "Set1")[seq_along(all_profiles)]
profile_col_map <- setNames(set1_cols, all_profiles)

# Build one radar panel per profile using facet_wrap on a "Facet" column
# Each panel: all profiles with their own colour; focal = bold+filled, others = thin+faint
radar_closed_facets <- purrr::map_dfr(all_profiles, \(focal) {
  radar_closed |>
    mutate(Facet     = focal,
           is_focal  = Profile == focal,
           lwd       = ifelse(is_focal, 1.2, 0.3),
           line_col  = profile_col_map[Profile],
           fill_col  = ifelse(is_focal, profile_col_map[Profile], NA_character_),
           poly_alpha = ifelse(is_focal, 0.18, 0.0))
})

radar_long_facets <- purrr::map_dfr(all_profiles, \(focal) {
  radar_long |>
    mutate(Facet    = focal,
           is_focal = Profile == focal,
           pt_col   = profile_col_map[Profile],
           pt_size  = ifelse(is_focal, 2.5, 0.8))
})

# Annotation label placed at centre-bottom of each facet
label_df <- profile_counts |>
  left_join(tibble(Profile = all_profiles, col = set1_cols), by = "Profile") |>
  rename(Facet = Profile)

p_radar <- ggplot() +
  # Grid circles
  geom_path(data = mutate(grid_circles, Facet = list(all_profiles)) |> tidyr::unnest(Facet),
            aes(x = x, y = y, group = r),
            colour = "grey88", linewidth = 0.25) +
  # Spokes
  geom_segment(data = mutate(spokes, Facet = list(all_profiles)) |> tidyr::unnest(Facet),
               aes(x = 0, y = 0, xend = x1, yend = y1),
               colour = "grey80", linewidth = 0.3) +
  # Axis labels
  geom_text(data = mutate(axis_labels, Facet = list(all_profiles)) |> tidyr::unnest(Facet),
            aes(x = lx, y = ly, label = label),
            size = 2.5, lineheight = 0.85, fontface = "bold", colour = "grey30") +
  # Background profiles (thin, own colour, no fill)
  geom_polygon(data = filter(radar_closed_facets, !is_focal),
               aes(x = x, y = y, group = Profile, colour = line_col),
               fill = NA, linewidth = 0.3, alpha = 0.5, show.legend = FALSE) +
  # Focal profile (coloured, filled)
  geom_polygon(data = filter(radar_closed_facets, is_focal),
               aes(x = x, y = y, group = Profile, colour = line_col, fill = fill_col),
               alpha = 0.18, linewidth = 1.2, show.legend = FALSE) +
  # Points — background
  geom_point(data = filter(radar_long_facets, !is_focal),
             aes(x = x, y = y, colour = pt_col), size = 0.8, alpha = 0.5, show.legend = FALSE) +
  # Points — focal
  geom_point(data = filter(radar_long_facets, is_focal),
             aes(x = x, y = y, colour = pt_col), size = 2.5, show.legend = FALSE) +
  # N (%) label per facet
  geom_text(data = label_df,
            aes(x = 0, y = -1.5, label = label, colour = col),
            size = 3, fontface = "bold", show.legend = FALSE) +
  scale_colour_identity() +
  scale_x_continuous(expand = expansion(mult = 0.15)) +
  scale_fill_identity() +
  facet_wrap(~Facet, ncol = 5) +
  # coord_equal(xlim = c(-1.75, 1.75), ylim = c(-1.75, 1.75)) +
  theme_void() +
  theme(plot.margin = margin(10, 10, 10, 10),
        plot.title  = element_text(size = 14, face = "bold", hjust = 0.5),
        strip.text  = element_text(face = "bold", size = 9, colour = "grey20")) +
  labs(title = "Researcher Profiles")

p_radar
```

### Predictors

```{r}
data <- cbind(df, df_resprac_fac)

m <- brms::brm(Profile ~ s(Dem_Age, by = Dem_Gender),
               family = brms::categorical(),
               data = data |>
                 mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |>
                 filter(Dem_Gender %in% c("Female", "Male"), Dem_Age <= 65),
               draws = 3000,
               single_path_draws  = 3000,
               backend = "cmdstanr",
               algorithm = "pathfinder")

p_archetypes_pred1 <- estimate_relation(m, length = 40) |>
  ggplot(aes(x = Dem_Age, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Response,
                  group = interaction(Dem_Gender, Response)), alpha = 0.1) +
  geom_line(aes(color=Response, linetype = Dem_Gender), linewidth = 1) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Probability of Belonging to Each Profile", x = "Age",
       fill = "Profile", color = "Profile", linetype = "Gender",
       title = "Proportion of Profiles as a function of Gender and Age") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)) +
  facet_wrap(~Response) 
p_archetypes_pred1
```


#### Age and Gender

```{r}
#| message: false

run_models <- function(dat = data, f = "~ Dem_Gender * poly(Dem_Age, 2)", means="Dem_Gender") {
  models <- list()
  pred <- data.frame()
  mmeans <- data.frame()
  for(outcome in c("Open_Science", "Rigorous_Science", "Green_Science", "Slow_Science", "Ethical_Science")) {
    m_f <- brms::bf(as.formula(paste0(outcome, f)))
    
    params <- get_prior(m_f, data = dat)$coef
    params <- params[str_ends(params, "22")]
    
    priors <- brms::set_prior("normal(0, 1)", class = "b", coef = params) |>
      brms::validate_prior(m_f, data = dat)
    
    m <- brms::brm(m_f,
                   data = dat,
                   refresh =  0,
                   prior = priors,
                   draws = 3000,
                   single_path_draws  = 3000,
                   backend = "cmdstanr",
                   algorithm = "pathfinder")
    models[[outcome]] <- m
    
    pred <- rbind(pred, mutate(estimate_relation(m, length = 40), Outcome = str_replace(outcome, "_", " ")))
    mmeans <- rbind(mmeans, mutate(estimate_means(m, by=means), Outcome = str_replace(outcome, "_", " ")))
  }
  pred <- mutate(pred, Outcome = factor(Outcome, levels = c("Open Science", "Rigorous Science", "Slow Science", "Green Science", "Ethical Science")))
  mmeans <- mutate(mmeans, Outcome = factor(Outcome, levels = c("Open Science", "Rigorous Science", "Slow Science", "Green Science", "Ethical Science")))
  list(pred=pred, mmeans=mmeans)
}
 

rez <- data |>
  mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |>
  filter(Dem_Gender %in% c("Female", "Male"), Dem_Age <= 65) |> 
  run_models(f = "~ Dem_Gender * poly(Dem_Age, 2)", means="Dem_Gender")



p_resval_pred1 <- rez$pred |>
  ggplot(aes(x = Dem_Age, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Outcome,
                  group = interaction(Dem_Gender, Outcome)), alpha = 0.1) +
  geom_line(aes(color=Outcome, linetype = Dem_Gender), linewidth = 1) +
  ggside::geom_xsidedensity(data = data |>
    mutate(Dem_Age = ifelse(is.na(Dem_Age), mean(df$Dem_Age, na.rm = TRUE), Dem_Age)) |>
    filter(Dem_Gender %in% c("Female", "Male"), Dem_Age <= 65), aes(linetype = Dem_Gender),
    show.legend = FALSE) +
  ggside::geom_ysidesegment(data=rez$mmeans, aes(x = Dem_Gender, xend = Dem_Gender, 
                                                 y = CI_low, yend = CI_high, color = Outcome,
                                                 linetype = Dem_Gender), linewidth = 0.5) +
  ggside::geom_ysidepoint(data = rez$mmeans, 
                            aes(x = Dem_Gender, y = Median, color = Outcome)) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  scale_colour_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  scale_fill_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Research Value", x = "Age",
       fill = "Profile", color = "Profile", linetype = "Gender",
       title = "Age and Gender") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0)) +
  ggside::theme_ggside_void() +
  facet_wrap(~Outcome, ncol = 5) 
p_resval_pred1
```

#### Carrer worry


```{r}
rez <- data |> 
  run_models(f = "~ Work_Career_Stage * poly(WB_Carrer_worry, 2)", means="Work_Career_Stage")

p_resval_pred2 <- rez$pred |>
  ggplot(aes(x = WB_Carrer_worry, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Outcome,
                  group = interaction(Work_Career_Stage, Outcome)), alpha = 0.1) +
  geom_line(aes(color=Outcome, linetype = Work_Career_Stage), linewidth = 1) +
  ggside::geom_xsidedensity(data = filter(data, !is.na(Work_Career_Stage)), aes(linetype = Work_Career_Stage),
    show.legend = FALSE) +
  ggside::geom_ysidesegment(data=rez$mmeans, aes(x = Work_Career_Stage, xend = Work_Career_Stage, 
                                                 y = CI_low, yend = CI_high, color = Outcome,
                                                 linetype = Work_Career_Stage), linewidth = 0.5) +
  ggside::geom_ysidepoint(data = rez$mmeans, 
                            aes(x = Work_Career_Stage, y = Median, color = Outcome)) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  scale_colour_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  scale_fill_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  scale_x_continuous(labels = scales::percent_format()) +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Research Value", x = "Career Worry",
       fill = "Profile", color = "Profile", linetype = "Career Stage",
       title = "Career Stage and Career Worry") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0)) +
  ggside::theme_ggside_void() + 
  facet_wrap(~Outcome, ncol = 5) 
p_resval_pred2
```

#### Research Time

```{r}
rez <- data |> 
  run_models(f = "~ Work_Career_Stage * poly(WB_Time_research, 2)", means="Work_Career_Stage")

p_resval_pred3 <- rez$pred |>
  ggplot(aes(x = WB_Time_research, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill=Outcome,
                  group = interaction(Work_Career_Stage, Outcome)), alpha = 0.1) +
  geom_line(aes(color=Outcome, linetype = Work_Career_Stage), linewidth = 1) +
  ggside::geom_xsidedensity(data = filter(data, !is.na(Work_Career_Stage)), aes(linetype = Work_Career_Stage),
    show.legend = FALSE) +
  ggside::geom_ysidesegment(data=rez$mmeans, aes(x = Work_Career_Stage, xend = Work_Career_Stage, 
                                                 y = CI_low, yend = CI_high, color = Outcome,
                                                 linetype = Work_Career_Stage), linewidth = 0.5) +
  ggside::geom_ysidepoint(data = rez$mmeans, 
                            aes(x = Work_Career_Stage, y = Median, color = Outcome)) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  scale_colour_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  scale_fill_manual(values = c("Open Science" = "#2196F3", "Rigorous Science" = "#3F51B5", "Green Science" = "#4CAF50",
                      "Slow Science" = "#FF9800", "Ethical Science" = "#9C27B0"), guide = "none") +
  scale_x_continuous(labels = scales::percent_format()) +
  guides(linetype = guide_legend(override.aes = list(linewidth = 0.3))) +
  labs(y = "Research Value", x = "Research Time",
       fill = "Profile", color = "Profile", linetype = "Career Stage",
       title = "Career Stage and Research Time") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0)) +
  ggside::theme_ggside_void() + 
  facet_wrap(~Outcome, ncol = 5) 
p_resval_pred3
```

## Figures

### Sample

```{r fig_sample}
#| fig-width: 9
#| fig-height: 12
#| warning: false

(p_age + p_children) / 
  (p_discipline + p_position) / 
  patchwork::wrap_elements(p_country) +
  plot_layout(heights = c(0.25, 0.3, 0.45)) +
  plot_annotation(
    title = paste0("Sample (N = ", nrow(df), ")"),
    theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0.5))
  )

# (p_position | p_country) / (p_time | p_career) +
#   plot_layout(heights = c(0.5, 0.5)) +
#   plot_annotation(title = "Demographics", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0)))
```

### Descriptive

```{r fig_descriptive}
#| fig-width: 7
#| fig-height: 10
#| warning: false

p_os_help / ss_def / ss_feas  + 
  # plot_layout(heights = c(0.6, 0.4)) +
  plot_annotation(title = "Descriptive", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0.5)))
```



### Structure of Research Values

```{r fig_structure}
#| fig-width: 13
#| fig-height: 16
#| warning: false

(wrap_elements(p_cor + 
                scale_x_discrete(expand = expansion(mult = c(0, 0.2))) +
                theme(panel.grid.major = element_blank())) | wrap_elements(p_resprac)) / 
  wrap_elements(p_cfa) /
  wrap_elements(p_radar) +
  plot_layout(heights = c(0.45, 0.3, 0.25)) +
  plot_annotation(title = "Researcher Profiles", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0.5)))
```

### Predictors of Research Values


```{r fig_preds}
#| fig-width: 10
#| fig-height: 10
#| warning: false

p_resval_pred1 /
  p_resval_pred2 / 
  p_resval_pred3 +
  # plot_layout(guides = "collect") +
  plot_annotation(title = "Research Values", theme = theme(plot.title = element_text(size = 18, face = "bold.italic", hjust = 0.5)))
```
